### 2024-12-01 reports/paper_outputs_Dec_2024.qmd
upload code files 01.12.24

---
title: "Outputs - civil servants' survey"
subtitle: "version 2"
author: "Saar Alon-Barkat"
date: "`r Sys.time()`"
format:
  html:
    self-contained: true
    page-layout: full
    code-fold: true
    toc: true
    toc-location: left
execute:
  message: false
  warning: false
  cache: true
---

```{r hebrew setup}

Sys.setlocale("LC_ALL", "Hebrew")
```

```{r libraries}
library(tidyverse)
library(haven)
library(ggplot2)
library(reshape2)
library(ggthemes)
library(dplyr)
library(qualtRics)
library(tidyr)
library(stringr)
library(gridExtra)
library(scales)
library(gtsummary)
library(psy)
library(labelled)
library(rtlr)
library(multilevel)
library(mediation)
library(lavaan)
library(semhelpinghands)
library(semPlot)

set.seed(2023)
```

```{r}
#source("Operationalization_31.7.R")

```

# Descriptive

duration
```{r}
new_data %>% 
  filter((ranking !="junior") %>% replace_na(TRUE)) %>% 
  filter(INTENT_EXIT_2>0|
          PROJECT_EFFORT>0|
           PROJECT_VOICE>0) %>% 
  dplyr::select(Duration__in_seconds_) %>%  
  summary()

618/60

```

## Table 1 - Characteristics of survey sample and research population
```{r}
data_for_analysis_senior %>% data_frame()%>%
  dplyr::select(tenure,
         position_type,
         ranking,
         gender,
         age,
         education,
         religiosity,
         jurist)  %>%
  gtsummary::tbl_summary()
```

## CFA - Measurement model

one factor model 
- Indepandant variables: 
PAST_INFLUENCE = "Q4_1", "Q4_2", "Q4_3"
PAST_POLITICIZATION = "Q10_1", "Q10_2", "Q10_3"
PAST_EFFORT = "Q19"
PAST_VOICE ="Q22_1", "Q22_2", "Q22_3"
BACKSLIDING_2 =  "Q15_rescale", "Q16_1", "Q16_2", "Q16_3","Q16_4","Q16_5"
PROJECT_POLITICIZATION = "Q_11"
PROJECT_INFLUENCE = "Q_5"

1-factor model
```{r}
cfa.model.1factor <-
  'one_factor =~ Q4_1+ Q4_2+ Q4_3 + Q10_1+ Q10_2+ Q10_3 + PAST_EFFORT + Q22_1+ Q22_2+ Q22_3 + Q15+ Q16_1+ Q16_2+ Q16_3+ Q16_4+ Q16_5 + PROJECT_POLITICIZATION + PROJECT_INFLUENCE'

fit.cfa.model.1factor <- cfa(cfa.model.1factor,# model formula,
                             data = data_for_analysis_senior,
                             se = "robust",
                             std.lv = T)

summary(fit.cfa.model.1factor, fit.measures = TRUE, standardize = TRUE)
```

7-factor model (Table B1)
```{r}
cfa.model.7factor <-
  'past_influence =~ Q4_1+ Q4_2+ Q4_3 
   past_politicization =~ Q10_1+ Q10_2+ Q10_3
   past_effort =~ PAST_EFFORT
   past_voice =~ Q22_1+ Q22_2+ Q22_3
   backsliding_2=~ Q16_1+ Q16_2+ Q16_3+ Q16_4+ Q16_5 + Q15
   project_politicization =~ PROJECT_POLITICIZATION
   project_influence =~ PROJECT_INFLUENCE'

fit.cfa.model.7factor <- cfa(cfa.model.7factor,# model formula,
                             data = data_for_analysis_senior,
                             se = "robust",
                             std.lv = T)

summary(fit.cfa.model.7factor, fit.measures = TRUE, standardize = TRUE)
```

```{r}
anova(fit.cfa.model.7factor,fit.cfa.model.1factor)
```

## Table 2: descriptive statistics

```{r}
t1 <- data_for_analysis_senior %>% 
  dplyr::select(
                PAST_INFLUENCE,
                PAST_POLITICIZATION,
                PAST_EFFORT,
                PAST_VOICE,
                BACKSLIDING_2,
                PROJECT_POLITICIZATION,
                PROJECT_INFLUENCE) %>%

  pivot_longer(cols = PAST_INFLUENCE:PROJECT_INFLUENCE) %>% 
  drop_na(value) %>% 
  mutate(name = name %>% car::recode("'BACKSLIDING_2' = '1. Perceived democratic backsliding';
      'PROJECT_POLITICIZATION' = '2. Expected politicization';  
      'PROJECT_INFLUENCE' = '3. Expected influence'; 
      'PAST_POLITICIZATION' = '4. Past politicization';
      'PAST_INFLUENCE' = '5. Past influence';
      'PAST_VOICE' = '6. Past voice';
      'PAST_EFFORT' = '7. Past work effort'"))

t1 %>%   group_by(name) %>% 
  dplyr::summarise(n = n(),
            Median = median(value,na.rm = T) %>% round(3),
            Mean = mean(value,na.rm = T) %>% round(3),
            SD = sd(value,na.rm = T) %>% round(3)) %>% 
    kableExtra::kable() %>% 
    kableExtra::kable_styling(bootstrap_options = c("condensed"),
                full_width = F,
                position = "left")
```

correlations between IVs
```{r}

data_for_analysis_senior %>% 
  dplyr::select(
                BACKSLIDING_2,
                PROJECT_POLITICIZATION,
                PROJECT_INFLUENCE,
                PAST_POLITICIZATION,
                PAST_INFLUENCE,
                PAST_VOICE,
                PAST_EFFORT) %>% 
  sjPlot::tab_corr(triangle = "lower",
                   #show.p = FALSE,
                   fade.ns = FALSE,
                   var.labels = str_c("(",1:7,")"))
```

## Figure 1

## Figure 2

# Main models

## OLS - no controls

Model for expected politicization & influence

```{r}
predictor_labels <- c(
  "BACKSLIDING_2" = "Democratic backsliding",
  "PAST_POLITICIZATION" = "Past politicization",
  "PAST_INFLUENCE" = "Past influence",
  "PROJECT_POLITICIZATION" = "Expected politicization",
  "PROJECT_INFLUENCE" = "Expected influence",
  "PAST_VOICE" = "Past voice",
  "PAST_EFFORT" = "Past work effort"
)
```

```{r}
politicization_mod1 <- lm(PROJECT_POLITICIZATION ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
            data=data_for_analysis_senior)

influence_mod1 <- politicization_mod1 %>%  update(PROJECT_INFLUENCE~.)

sjPlot::tab_model(politicization_mod1,influence_mod1,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                  dv.labels = c("Expected politicization","Expected influence"),
                  order.terms = c(2:4,1))

```

Model for exit, voice and work
```{r}
exit_mod1 <- lm(INTENT_EXIT_2 ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
            data=data_for_analysis_senior)

exit_mod2 <- exit_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)

voice_mod1 <- exit_mod1 %>% update(PROJECT_VOICE~.+ PAST_VOICE)
voice_mod2 <- voice_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)

work_mod1 <- exit_mod1 %>% update(PROJECT_EFFORT~.+ PAST_EFFORT)
work_mod2 <- work_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)

sjPlot::tab_model(exit_mod1,exit_mod2,
                  voice_mod1,voice_mod2,
                  work_mod1,work_mod2,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                  dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2),
                  order.terms = c(2,5:6,3:4,7:8,1))

```

```{r}
sjPlot::tab_model(exit_mod1,exit_mod2,
                  voice_mod1,voice_mod2,
                  work_mod1,work_mod2)
```

Model for exit, voice and work
```{r}
exit_mod1 <- lm(INTENT_EXIT_2 ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
            data=data_for_analysis_senior)
exit_mod2 <- exit_mod1 %>%  update(.~. + PROJECT_POLITICIZATION)
exit_mod3 <- exit_mod1 %>%  update(.~. + PROJECT_INFLUENCE)
exit_mod4 <- exit_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)

sjPlot::tab_model(exit_mod1,exit_mod2,exit_mod3,exit_mod4,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,#,
                  dv.labels = rep(c("Exit intention"),each=4),
                  #dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2),
                  order.terms = c(2,5:6,3:4,1))

```

```{r}
voice_mod1 <- exit_mod1 %>% update(PROJECT_VOICE~.+ PAST_VOICE)
voice_mod2 <- voice_mod1 %>%  update(.~. + PROJECT_POLITICIZATION)
voice_mod3 <- voice_mod1 %>%  update(.~. + PROJECT_INFLUENCE)
voice_mod4 <- voice_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)

sjPlot::tab_model(voice_mod1,voice_mod2,voice_mod3,voice_mod4,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                  dv.labels = rep(c("Voice intention"),each=4),
                  #dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2),
                  order.terms = c(2,6:7,3:5,1))

```

```{r}
work_mod1 <- exit_mod1 %>% update(PROJECT_EFFORT~.+ PAST_EFFORT)
work_mod2 <- work_mod1 %>%  update(.~. + PROJECT_POLITICIZATION)
work_mod3 <- work_mod1 %>%  update(.~. + PROJECT_INFLUENCE)
work_mod4 <- work_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)

sjPlot::tab_model(work_mod1,work_mod2,work_mod3,work_mod4,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                  dv.labels = rep(c("Work effort intention"),each=4),
                  #dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2),
                  order.terms = c(2,6:7,3:5,1))

```

## Causal mediation analysis

Exit

```{r}
# Load necessary package
library(mediation)
set.seed(2023)

t1 <- data_for_analysis_senior %>% 
  drop_na(BACKSLIDING_2,INTENT_EXIT_2,PROJECT_VOICE,PROJECT_EFFORT,PROJECT_POLITICIZATION,PROJECT_INFLUENCE)

# Mediator 1 model
med1_model <- lm(PROJECT_POLITICIZATION ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
            data=t1)

# Mediator 2 model
med2_model <- lm(PROJECT_INFLUENCE ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
            data=t1)

# Outcome model med 1
outcome_model_1 <-
  lm(INTENT_EXIT_2 ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE +
            PROJECT_POLITICIZATION,
            data=t1)

# Outcome model med 2
outcome_model_2 <-
  lm(INTENT_EXIT_2 ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE +
            PROJECT_INFLUENCE,
            data=t1)

# Mediation analysis for the first mediator with bootstrapping
mediation_result_exit_politicization <-
  mediate(
    med1_model,
    outcome_model_1,
    treat = "BACKSLIDING_2",
    mediator = "PROJECT_POLITICIZATION",
    boot = TRUE,
    sims = 1000
  )

# Mediation analysis for the second mediator with bootstrapping
mediation_result_exit_influence <-
  mediate(
    med2_model,
    outcome_model_2,
    treat = "BACKSLIDING_2",
    mediator = "PROJECT_INFLUENCE",
    boot = TRUE,
    sims = 1000
  )

# Summary of the results
```

```{r}
summary(mediation_result_exit_politicization) 
```

```{r}
summary(mediation_result_exit_influence)
```

Voice

```{r}

# Outcome model med 1
outcome_model_1 <-
  lm(PROJECT_VOICE ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE +
            PROJECT_POLITICIZATION,
            data=t1)

# Outcome model med 2
outcome_model_2 <-
  lm(PROJECT_VOICE ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE +
            PROJECT_INFLUENCE,
            data=t1)

# Mediation analysis for the first mediator with bootstrapping
mediation_result_voice_politicization <-
  mediate(
    med1_model,
    outcome_model_1,
    treat = "BACKSLIDING_2",
    mediator = "PROJECT_POLITICIZATION",
    boot = TRUE,
    sims = 1000
  )

# Mediation analysis for the second mediator with bootstrapping
mediation_result_voice_influence <-
  mediate(
    med2_model,
    outcome_model_2,
    treat = "BACKSLIDING_2",
    mediator = "PROJECT_INFLUENCE",
    boot = TRUE,
    sims = 1000
  )

# Summary of the results
```

```{r}
summary(mediation_result_voice_politicization)
```

```{r}
summary(mediation_result_voice_influence)
```

Effort

```{r}

# Outcome model med 1
outcome_model_1 <-
  lm(PROJECT_EFFORT ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE + PAST_EFFORT + 
            PROJECT_POLITICIZATION,
            data=t1)

# Outcome model med 2
outcome_model_2 <-
  lm(PROJECT_EFFORT ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE + PAST_EFFORT + 
            PROJECT_INFLUENCE,
            data=t1)

# Mediation analysis for the first mediator with bootstrapping
mediation_result_work_politicization <-
  mediate(
    med1_model,
    outcome_model_1,
    treat = "BACKSLIDING_2",
    mediator = "PROJECT_POLITICIZATION",
    boot = TRUE,
    sims = 1000
  )

# Mediation analysis for the second mediator with bootstrapping
mediation_result_work_influence <-
  mediate(
    med2_model,
    outcome_model_2,
    treat = "BACKSLIDING_2",
    mediator = "PROJECT_INFLUENCE",
    boot = TRUE,
    sims = 1000
  )

# Summary of the results
```

```{r}
summary(mediation_result_work_politicization)
```

```{r}
summary(mediation_result_work_influence)
```

## Descripive illustration

```{r}
t1 <- data_for_analysis_senior %>% 
  mutate(high_backsliding = case_when(
    BACKSLIDING_2>0.84 ~ 1,
    BACKSLIDING_2<=0.84 ~ 0
  ),
  high_exit = case_when(
    INTENT_EXIT_2>0.5 ~ 1,
    INTENT_EXIT_2<=0.5 ~ 0
  ),
  low_voice = case_when(
    PROJECT_VOICE<0.5 ~ 1,
    PROJECT_VOICE>=0.5 ~ 0
  ),
  low_effort = case_when(
    PROJECT_EFFORT<0.5 ~ 1,
    PROJECT_EFFORT>=0.5 ~ 0
  ),

  )

t1 %>% count(PROJECT_EFFORT,low_effort)

t1 %>% 
  group_by(high_backsliding) %>% 
  summarise(mean(high_exit,na.rm=T),
            mean(low_voice,na.rm=T),
            mean(low_effort,na.rm=T))

#exit
0.3558282/0.1988950

#voice
0.2760736/0.1739130

#work effort
0.2787879/0.1746032
```
## Model prediction

```{r}
pd_data <- data.frame(BACKSLIDING_2 = seq(0, 1, length = 100),
                 PAST_POLITICIZATION = rep(mean(data_for_analysis_senior$PAST_POLITICIZATION,na.rm=T), length = 100),
                 PAST_INFLUENCE = rep(mean(data_for_analysis_senior$PAST_INFLUENCE,na.rm=T), length = 100),
                 PAST_VOICE = rep(mean(data_for_analysis_senior$PAST_VOICE,na.rm=T), length = 100),
                 PAST_EFFORT = rep(mean(data_for_analysis_senior$PAST_EFFORT,na.rm=T), length = 100))

pd_data_exit <- pd_data %>% 
  cbind(predict(exit_mod1, pd_data, se.fit = TRUE)[1:2]) %>% 
  transform(
    Upper = fit + (1.96 * se.fit),
    Lower = fit - (1.96 * se.fit))

pd_data_voice <- pd_data %>% 
  cbind(predict(voice_mod1, pd_data, se.fit = TRUE)[1:2]) %>% 
  transform(
    Upper = fit + (1.96 * se.fit),
    Lower = fit - (1.96 * se.fit))

pd_data_work <- pd_data %>% 
  cbind(predict(work_mod1, pd_data, se.fit = TRUE)[1:2]) %>% 
  transform(
    Upper = fit + (1.96 * se.fit),
    Lower = fit - (1.96 * se.fit))

```

```{r,fig.width=10,fig.height=4}
p1 <- data_for_analysis_senior %>% 
  ggplot(aes(x=BACKSLIDING_2,y=INTENT_EXIT_2))+
  geom_jitter(width=0,height = 0.02,alpha=0.3,size=2,color="orange")+
  labs(x="Perceived democratic backsliding",
       y="Exit intention")+
  #geom_smooth(method="lm")+
    geom_line(data = pd_data_exit, aes(y = fit, x = BACKSLIDING_2),size=2) +
  geom_line(
    data = pd_data_exit,
    aes(y = Lower),
    size = 0.1,
    #color = 'gray10',
    linetype = "longdash"
  ) +
  geom_line(
    data = pd_data_exit,
    aes(y = Upper),
    size = 0.1,
    #color = 'gray10',
    linetype = "longdash"
  ) +
  theme_classic()

p2 <- data_for_analysis_senior %>% 
  ggplot(aes(x=BACKSLIDING_2,y=PROJECT_VOICE))+
  geom_jitter(width=0,height = 0.02,alpha=0.3,size=2,color="orange")+
  labs(x="Perceived democratic backsliding",
       y="Voice intention")+
  #geom_smooth(method="lm")+
    geom_line(data = pd_data_voice, aes(y = fit, x = BACKSLIDING_2),size=2) +
  geom_line(
    data = pd_data_voice,
    aes(y = Lower),
    size = 0.1,
    #color = 'gray10',
    linetype = "longdash"
  ) +
  geom_line(
    data = pd_data_voice,
    aes(y = Upper),
    size = 0.1,
    #color = 'gray10',
    linetype = "longdash"
  ) +
  theme_classic()

p3 <- data_for_analysis_senior %>% 
  ggplot(aes(x=BACKSLIDING_2,y=PROJECT_EFFORT))+
  geom_jitter(width=0,height = 0.02,alpha=0.3,size=2,color="orange")+
  labs(x="Perceived democratic backsliding",
       y="Work effort intention")+
  #geom_smooth(method="lm")+
    geom_line(data = pd_data_work, aes(y = fit, x = BACKSLIDING_2),size=2) +
  geom_line(
    data = pd_data_work,
    aes(y = Lower),
    size = 0.1,
    #color = 'gray10',
    linetype = "longdash"
  ) +
  geom_line(
    data = pd_data_work,
    aes(y = Upper),
    size = 0.1,
    #color = 'gray10',
    linetype = "longdash"
  ) +
  theme_classic()

ggpubr::ggarrange(p1,p2,p3,
          ncol=3,
          label.x = "Perceived democratic backsliding")
```

# Exit 1

```{r}
data_for_analysis_senior %>% count(INTENT_EXIT_1)
```
```{r}
data_for_analysis_senior %>%
  mutate(INTENT_EXIT_1_lab = case_when(
    INTENT_EXIT_1==0 ~ "1. ...to leave government as soon as possible",
    INTENT_EXIT_1==0.25 ~ "2. ...to leave government during the coming year",
    INTENT_EXIT_1==0.5 ~ "3. ...to stay in government, a least for the next two years",
    INTENT_EXIT_1==0.75 ~ "4. ...to stay in government, at least for the next five years",
    INTENT_EXIT_1==1 ~ "5. ...to stay in government for the rest of my career",

  )) %>%  
  dplyr::select(INTENT_EXIT_1_lab) %>% 
  tbl_summary()
```

```{r}

t1<- data_for_analysis_senior %>%
  mutate(INTENT_EXIT_1_lab = case_when(
    INTENT_EXIT_1==0 ~ "1. ...leave government as soon as possible",
    INTENT_EXIT_1==0.25 ~ "2. ...leave government during the coming year",
    INTENT_EXIT_1==0.5 ~ "3. ...stay in government, a least for the next two years",
    INTENT_EXIT_1==0.75 ~ "4. ...stay in government, at least for the next five years",
    INTENT_EXIT_1==1 ~ "5. ...stay in government for the rest of my career",

  )) %>%  
  drop_na(INTENT_EXIT_1_lab) %>% 
  group_by(INTENT_EXIT_1_lab) %>%
  summarize(n=n())%>%
mutate(freq=(n/sum(n))%>%round(3))%>%
  mutate(freq.lab=str_c(100*freq,"%"))

t1%>% 
  #drop_na(trust_in_gov_lab)%>%
  ggplot(aes(x=factor(INTENT_EXIT_1_lab),y=n))+
  geom_col(alpha=0.8,fill="lightblue")+
  geom_text(aes(label=freq.lab),colour="gray20",size=3)+
  labs(title="",x="",y="Frequency")+
  #facet_wrap(vars(name),ncol = 3)+
  coord_cartesian(ylim = c(0,0.5))+
  coord_flip()  +
  theme_classic() 
```

```{r}
data_for_analysis_senior %>% 
    mutate(INTENT_EXIT_1_lab = case_when(
    INTENT_EXIT_1==0 ~ "1. ...leave government as soon as possible",
    INTENT_EXIT_1==0.25 ~ "2. ...leave government during the coming year",
    INTENT_EXIT_1==0.5 ~ "3. ...stay in government, a least for the next two years",
    INTENT_EXIT_1==0.75 ~ "4. ...stay in government, at least for the next five years",
    INTENT_EXIT_1==1 ~ "5. ...stay in government for the rest of my career",

  )) %>%  
  ggplot(aes(x=factor(INTENT_EXIT_1_lab),y=INTENT_EXIT_2))+
  #geom_boxplot()#+
  stat_summary(
    fun.y = mean,
    geom = "point",
    alpha = 0.5,
    size = 2
  ) +
    stat_summary(
    fun.data = mean_cl_normal,
    geom = "errorbar",
    fun.args = list(conf.int = 0.95),
    alpha = 0.5,
    width = 0.1,
    size = 1) +
     coord_flip()+
  labs(title="",x="Exit intention (first measure)",y="Exit intention (second measure)",fill="")+
  #facet_wrap(vars(wave))+
  theme_classic() 
```
```{r}
data_for_analysis_senior %>% remove_labels() %>% 
  dplyr::select(INTENT_EXIT_1,
                INTENT_EXIT_2,
                BACKSLIDING_2, 
                PROJECT_VOICE,
                PROJECT_EFFORT,
                PROJECT_POLITICIZATION,
                PROJECT_INFLUENCE,
                PAST_POLITICIZATION,
                PAST_INFLUENCE) %>% 
  sjPlot::tab_corr(triangle = "lower",
                   show.p = FALSE,
                   fade.ns = FALSE)
```

```{r}
exit_mod1 <- lm(INTENT_EXIT_1 ~ 
            BACKSLIDING_2,
            data=data_for_analysis_senior)

exit_mod2 <- exit_mod1 %>% update(.~.+ PROJECT_POLITICIZATION + PROJECT_INFLUENCE)

exit_mod3 <- exit_mod1 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)

exit_mod4 <- exit_mod2 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)

#Table A8
sjPlot::tab_model(exit_mod1,exit_mod2,
                  exit_mod3,exit_mod4,
                  show.ci = F,
                  show.se = T,
                  collapse.se = T,
                  terms = c("(Intercept)",
                            "BACKSLIDING_2",
                            "PROJECT_POLITICIZATION",
                            "PROJECT_INFLUENCE"))

```

```{r}
exit_mod1 <- lm(INTENT_EXIT_2 ~ 
            BACKSLIDING_2,
            data=data_for_analysis_senior)

exit_mod2 <- exit_mod1 %>% update(.~.+ PROJECT_POLITICIZATION + PROJECT_INFLUENCE)

exit_mod3 <- exit_mod1 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)

exit_mod4 <- exit_mod2 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)

#Table A8
sjPlot::tab_model(exit_mod1,exit_mod2,
                  exit_mod3,exit_mod4,
                  show.ci = F,
                  show.se = T,
                  collapse.se = T,
                  terms = c("(Intercept)",
                            "BACKSLIDING_2",
                            "PROJECT_POLITICIZATION",
                            "PROJECT_INFLUENCE"))

```

## Controls

Model for expected politicization & influence

```{r}
predictor_labels <- c(
  "BACKSLIDING_2" = "Democratic backsliding",
  "PAST_POLITICIZATION" = "Past politicization",
  "PAST_INFLUENCE" = "Past influence",
  "PROJECT_POLITICIZATION" = "Expected politicization",
  "PROJECT_INFLUENCE" = "Expected influence",
  "PAST_VOICE" = "Past voice",
  "PAST_EFFORT" = "Past work effort"
)
```

```{r}
politicization_mod1 <- lm(PROJECT_POLITICIZATION ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist,
            data=data_for_analysis_senior)
politicization_mod1_relig <- politicization_mod1 %>% update(.~.+religiosity)

influence_mod1 <- politicization_mod1 %>%  update(PROJECT_INFLUENCE~.)
influence_mod1_relig <- influence_mod1 %>% update(.~.+religiosity)

sjPlot::tab_model(politicization_mod1,politicization_mod1_relig,
                  influence_mod1,influence_mod1_relig,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels)#,
                  dv.labels = c("Expected politicization","Expected influence")#,
                  #order.terms = c(2:4,1)
                  )

```

Model for exit, voice and work
```{r}
exit_mod1 <- lm(INTENT_EXIT_2 ~ 
            #BACKSLIDING_2 +   
              PAST_POLITICIZATION + PAST_INFLUENCE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist,
            data=data_for_analysis_senior)
exit_mod1_relig <- exit_mod1 %>% update(.~.+religiosity)

voice_mod1 <- exit_mod1 %>% update(PROJECT_VOICE~.+ PAST_VOICE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)
voice_mod1_relig <- voice_mod1 %>% update(.~.+religiosity)

work_mod1 <- exit_mod1 %>% update(PROJECT_EFFORT~.+ PAST_EFFORT+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)
work_mod1_relig <- work_mod1 %>% update(.~.+religiosity)

sjPlot::tab_model(exit_mod1,exit_mod1_relig,
                  voice_mod1,voice_mod1_relig,
                  work_mod1,work_mod1_relig,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                  dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2))

```

```{r}
sjPlot::tab_model(exit_mod1,exit_mod2,
                  voice_mod1,voice_mod2,
                  work_mod1,work_mod2)
```

Model for exit, voice and work
```{r}
exit_mod1 <- lm(INTENT_EXIT_2 ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
            data=data_for_analysis_senior)
exit_mod2 <- exit_mod1 %>%  update(.~. + PROJECT_POLITICIZATION)
exit_mod3 <- exit_mod1 %>%  update(.~. + PROJECT_INFLUENCE)
exit_mod4 <- exit_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)

sjPlot::tab_model(exit_mod1,exit_mod2,exit_mod3,exit_mod4,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,#,
                  dv.labels = rep(c("Exit intention"),each=4),
                  #dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2),
                  order.terms = c(2,5:6,3:4,1))

```

```{r}
voice_mod1 <- exit_mod1 %>% update(PROJECT_VOICE~.+ PAST_VOICE)
voice_mod2 <- voice_mod1 %>%  update(.~. + PROJECT_POLITICIZATION)
voice_mod3 <- voice_mod1 %>%  update(.~. + PROJECT_INFLUENCE)
voice_mod4 <- voice_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)

sjPlot::tab_model(voice_mod1,voice_mod2,voice_mod3,voice_mod4,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                  dv.labels = rep(c("Voice intention"),each=4),
                  #dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2),
                  order.terms = c(2,6:7,3:5,1))

```

```{r}
work_mod1 <- exit_mod1 %>% update(PROJECT_EFFORT~.+ PAST_EFFORT)
work_mod2 <- work_mod1 %>%  update(.~. + PROJECT_POLITICIZATION)
work_mod3 <- work_mod1 %>%  update(.~. + PROJECT_INFLUENCE)
work_mod4 <- work_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)

sjPlot::tab_model(work_mod1,work_mod2,work_mod3,work_mod4,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                  dv.labels = rep(c("Work effort intention"),each=4),
                  #dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2),
                  order.terms = c(2,6:7,3:5,1))

```

### 2024-12-01 code/Operationalization.R

@@ -1,0 +1,387 @@
+########################
+#title: "Operationalization"
+#author: "Nir Kosti"
+#date: "`r Sys.time()`"
+########################
+
+
+# hebrew setup
+Sys.setlocale(category = "LC_ALL", locale = "Hebrew_Israel.1255")
+#rmarkdown setup
+knitr::opts_chunk$set(message = FALSE)
+#read relevant libraries 
+library(haven)
+library(scales)
+library(ggplot2)
+library(reshape2)
+library(ggthemes)
+library(dplyr)
+library(qualtRics)
+library(tidyr)
+library(stringr)
+library(gridExtra)
+library(openxlsx)
+library(scales)
+library(gtsummary)
+library(psy)
+library(lavaan)
+library(labelled)
+
+#read data with qualtRics 
+setwd("C:\\Users\\Nir\\Dropbox\\Civil Servants' Perceptions of Democratic Decline\\data\\raw data")
+data <- read_spss("survey_14.3.2023.sav")
+
+#create a new dataset with combined variables for men and women
+new_data <- data[, 1:19]
+
+#combine variables for men and women
+new_data$Q2 <- coalesce(data$Q2_cs_filter, data$Q2_f)
+
+#Q4 - influence past
+new_data$Q4_1 <- coalesce(data$Q4_influence_past_1, data$Q4_f_influence_past_1)
+new_data$Q4_2 <- coalesce(data$Q4_influence_past_2, data$Q4_f_influence_past_2)
+new_data$Q4_3 <-coalesce(data$Q4_influence_past_3, data$Q4_f_influence_past_3)
+
+#Q5 - influence future
+new_data$Q5 <- coalesce(data$Q5_influence_future, data$Q5_f_influence_futur)
+
+#Q6 - influence comments
+new_data$Q6 <- str_c(data$Q6_influence_comment, data$Q6_f_influence_comme)
+
+#Q10 - meritocracy - past
+new_data$Q10_1 <- coalesce(data$Q10_meritocracy_past_1, data$Q10_f_meritocracy_pa_1)
+new_data$Q10_2 <- coalesce(data$Q10_meritocracy_past_2, data$Q10_f_meritocracy_pa_2)
[…]

### 2024-12-01 code/Operationalization_with_weights.R

@@ -1,0 +1,521 @@
+########################
+#title: "Operationalization"
+#author: "Nir Kosti"
+#date: "`r Sys.time()`"
+########################
+
+
+# hebrew setup
+Sys.setlocale(category = "LC_ALL", locale = "Hebrew_Israel.1255")
+#rmarkdown setup
+knitr::opts_chunk$set(message = FALSE)
+#read relevant libraries 
+library(haven)
+library(scales)
+library(ggplot2)
+library(reshape2)
+library(ggthemes)
+library(dplyr)
+library(qualtRics)
+library(tidyr)
+library(stringr)
+library(gridExtra)
+library(openxlsx)
+library(scales)
+#library(gtsummary)
+library(psy)
+library(lavaan)
+library(labelled)
+
+#read data with qualtRics 
+setwd("C:\\Users\\nirko\\Dropbox\\Civil Servants' Perceptions of Democratic Decline\\data\\raw data")
+data <- read_spss("survey_14.3.2023.sav")
+
+#create a new dataset with combined variables for men and women
+new_data <- data[, 1:19]
+
+#combine variables for men and women
+new_data$Q2 <- coalesce(data$Q2_cs_filter, data$Q2_f)
+
+#Q4 - influence past
+new_data$Q4_1 <- coalesce(data$Q4_influence_past_1, data$Q4_f_influence_past_1)
+new_data$Q4_2 <- coalesce(data$Q4_influence_past_2, data$Q4_f_influence_past_2)
+new_data$Q4_3 <-coalesce(data$Q4_influence_past_3, data$Q4_f_influence_past_3)
+
+#Q5 - influence future
+new_data$Q5 <- coalesce(data$Q5_influence_future, data$Q5_f_influence_futur)
+
+#Q6 - influence comments
+new_data$Q6 <- str_c(data$Q6_influence_comment, data$Q6_f_influence_comme)
+
+#Q10 - meritocracy - past
+new_data$Q10_1 <- coalesce(data$Q10_meritocracy_past_1, data$Q10_f_meritocracy_pa_1)
+new_data$Q10_2 <- coalesce(data$Q10_meritocracy_past_2, data$Q10_f_meritocracy_pa_2)
[…]

### 2024-12-02 reports/paper_outputs_Dec_2024.qmd
Update paper_outputs_Dec_2024.qmd
Updating regression tables and main models

@@
             BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
-            data=data_for_analysis_senior)
+            data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))
 
@@
 ```
+
+## SEM models
+
+```{r}
+SEM_All <-'
+
+##Direct effects##
+INTENT_EXIT_2 ~ cp_ex*BACKSLIDING_2
+PROJECT_VOICE ~ cp_vc*BACKSLIDING_2 + PAST_VOICE
+PROJECT_EFFORT ~ cp_eff*BACKSLIDING_2 + PAST_EFFORT
+
+##Mediators##
+PROJECT_POLITICIZATION ~ a1*BACKSLIDING_2 + PAST_POLITICIZATION 
+PROJECT_INFLUENCE ~ a2*BACKSLIDING_2 + PAST_INFLUENCE
+
+INTENT_EXIT_2 ~ b1_ex*PROJECT_POLITICIZATION + PAST_POLITICIZATION
+INTENT_EXIT_2 ~ b2_ex*PROJECT_INFLUENCE + PAST_INFLUENCE
+
+PROJECT_VOICE ~ b1_vc*PROJECT_POLITICIZATION + PAST_POLITICIZATION
+PROJECT_VOICE ~ b2_vc*PROJECT_INFLUENCE + PAST_INFLUENCE
+
+PROJECT_EFFORT ~ b1_eff*PROJECT_POLITICIZATION + PAST_POLITICIZATION
+PROJECT_EFFORT ~ b2_eff*PROJECT_INFLUENCE + PAST_INFLUENCE
+
+## Indirect effects ##
+tot_ind_exit := abs(a1*b1_ex) + abs(a2*b2_ex)
+tot_ind_voice := abs(a1*b1_vc) + abs(a2*b2_vc)
+tot_ind_effort := abs(a1*b1_eff) + abs(a2*b2_eff)
+
+dir_backs_polit := a1
+dir_backs_inf := a2
+
+dir_backs_exit := cp_ex
+dir_polit_exit := b1_ex
+dir_infl_exit := b2_ex
+
+dir_backs_voice := cp_vc
+dir_polit_voice := b1_vc
+dir_infl_voice := b2_vc
+
+dir_backs_effort := cp_eff
+dir_proj_polit_effort := b1_eff
+dir_proj_infl_effort := b2_eff
+
+##indirect effects##
+ind_back_polit_exit := a1*b1_ex
+ind_back_infl_exit := a2*b2_ex
+
+ind_back_polit_voice := a1*b1_vc
+ind_back_infl_voice := a2*b2_vc
+
+ind_back_polit_effort := a1*b1_eff
+ind_back_infl_effort := a2*b2_eff
+
+##total effects##
+tot_back_exit := cp_ex + (a1*b1_ex) + (a2*b2_ex)
+tot_back_voice := cp_vc + (a1*b1_vc) + (a2*b2_vc)
+tot_back_effort := cp_eff + (a1*b1_eff) + (a2*b2_eff)
+
+##Correlations between mediators##
+PROJECT_POLITICIZATION~~PROJECT_INFLUENCE
+
+##Other correlations##
+PROJECT_POLITICIZATION~~PAST_INFLUENCE
+PROJECT_INFLUENCE~~PAST_POLITICIZATION
+PAST_POLITICIZATION~~PAST_INFLUENCE
+PAST_EFFORT~~PROJECT_POLITICIZATION
+PAST_EFFORT~~PROJECT_INFLUENCE
+
+##Contrasts
+c1v2_exit := (a1*b1_ex) - (a2*b2_ex)
+c1v2_voice := (a1*b1_vc) - (a2*b2_vc)
+c1v2_effort := (a1*b1_eff) - (a2*b2_eff)'
+
+fit_all <- sem(SEM_All, # model formula
+                se = "bootstrap",
+                missing="ML",
+                data = data_for_analysis_senior)# 
+```
+
+```{r}
+summary(fit_all, fit.measures=TRUE, standardized=TRUE)
+```
+
+```{r}
+parameterEstimates(fit_all, boot.ci.type	="basic", standardized = T, output = "text")
+```
+
+# Online appendix
 
@@
 ```
-## Model prediction
 
-```{r}
-pd_data <- data.frame(BACKSLIDING_2 = seq(0, 1, length = 100),
-                 PAST_POLITICIZATION = rep(mean(data_for_analysis_senior$PAST_POLITICIZATION,na.rm=T), length = 100),
-                 PAST_INFLUENCE = rep(mean(data_for_analysis_senior$PAST_INFLUENCE,na.rm=T), length = 100),
-                 PAST_VOICE = rep(mean(data_for_analysis_senior$PAST_VOICE,na.rm=T), length = 100),
-                 PAST_EFFORT = rep(mean(data_for_analysis_senior$PAST_EFFORT,na.rm=T), length = 100))
-
-pd_data_exit <- pd_data %>% 
-  cbind(predict(exit_mod1, pd_data, se.fit = TRUE)[1:2]) %>% 
-  transform(
-    Upper = fit + (1.96 * se.fit),
-    Lower = fit - (1.96 * se.fit))
-
-pd_data_voice <- pd_data %>% 
-  cbind(predict(voice_mod1, pd_data, se.fit = TRUE)[1:2]) %>% 
-  transform(
-    Upper = fit + (1.96 * se.fit),
-    Lower = fit - (1.96 * se.fit))
-
-pd_data_work <- pd_data %>% 
-  cbind(predict(work_mod1, pd_data, se.fit = TRUE)[1:2]) %>% 
-  transform(
-    Upper = fit + (1.96 * se.fit),
-    Lower = fit - (1.96 * se.fit))
-
-```
-
-```{r,fig.width=10,fig.height=4}
-p1 <- data_for_analysis_senior %>% 
-  ggplot(aes(x=BACKSLIDING_2,y=INTENT_EXIT_2))+
-  geom_jitter(width=0,height = 0.02,alpha=0.3,size=2,color="orange")+
-  labs(x="Perceived democratic backsliding",
-       y="Exit intention")+
-  #geom_smooth(method="lm")+
-    geom_line(data = pd_data_exit, aes(y = fit, x = BACKSLIDING_2),size=2) +
-  geom_line(
-    data = pd_data_exit,
-    aes(y = Lower),
-    size = 0.1,
-    #color = 'gray10',
-    linetype = "longdash"
-  ) +
-  geom_line(
-    data = pd_data_exit,
-    aes(y = Upper),
-    size = 0.1,
-    #color = 'gray10',
-    linetype = "longdash"
-  ) +
-  theme_classic()
-
-p2 <- data_for_analysis_senior %>% 
-  ggplot(aes(x=BACKSLIDING_2,y=PROJECT_VOICE))+
-  geom_jitter(width=0,height = 0.02,alpha=0.3,size=2,color="orange")+
-  labs(x="Perceived democratic backsliding",
-       y="Voice intention")+
-  #geom_smooth(method="lm")+
-    geom_line(data = pd_data_voice, aes(y = fit, x = BACKSLIDING_2),size=2) +
-  geom_line(
-    data = pd_data_voice,
-    aes(y = Lower),
-    size = 0.1,
-    #color = 'gray10',
-    linetype = "longdash"
-  ) +
-  geom_line(
-    data = pd_data_voice,
-    aes(y = Upper),
-    size = 0.1,
-    #color = 'gray10',
-    linetype = "longdash"
-  ) +
-  theme_classic()
-
-p3 <- data_for_analysis_senior %>% 
-  ggplot(aes(x=BACKSLIDING_2,y=PROJECT_EFFORT))+
-  geom_jitter(width=0,height = 0.02,alpha=0.3,size=2,color="orange")+
-  labs(x="Perceived democratic backsliding",
-       y="Work effort intention")+
-  #geom_smooth(method="lm")+
-    geom_line(data = pd_data_work, aes(y = fit, x = BACKSLIDING_2),size=2) +
-  geom_line(
-    data = pd_data_work,
-    aes(y = Lower),
-    size = 0.1,
-    #color = 'gray10',
-    linetype = "longdash"
-  ) +
-  geom_line(
-    data = pd_data_work,
-    aes(y = Upper),
-    size = 0.1,
-    #color = 'gray10',
-    linetype = "longdash"
-  ) +
-  theme_classic()
-
-ggpubr::ggarrange(p1,p2,p3,
-          ncol=3,
-          label.x = "Perceived democratic backsliding")
-```
-
-# Exit 1
+## Exit 1
 
@@
                   pred.labels = predictor_labels)#,
-                  dv.labels = c("Expected politicization","Expected influence")#,
-                  #order.terms = c(2:4,1)
-                  )
+                  dv.labels = c("Expected politicization","Expected influence")
 
@@
 exit_mod1 <- lm(INTENT_EXIT_2 ~ 
-            #BACKSLIDING_2 +   
+            BACKSLIDING_2 +   
               PAST_POLITICIZATION + PAST_INFLUENCE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist,
@@
 ```
-
-```{r}
-sjPlot::tab_model(exit_mod1,exit_mod2,
-                  voice_mod1,voice_mod2,
-                  work_mod1,work_mod2)
-```
-
-Model for exit, voice and work
-```{r}
-exit_mod1 <- lm(INTENT_EXIT_2 ~ 
-            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
-            data=data_for_analysis_senior)
-exit_mod2 <- exit_mod1 %>%  update(.~. + PROJECT_POLITICIZATION)
-exit_mod3 <- exit_mod1 %>%  update(.~. + PROJECT_INFLUENCE)
-exit_mod4 <- exit_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
-
-sjPlot::tab_model(exit_mod1,exit_mod2,exit_mod3,exit_mod4,
-                  show.ci = F,
-                  show.se = T,
-                  show.std = T,
-                  collapse.se = T,
-                  emph.p=F,
-                  string.est = "B",
-                  string.std = "Beta",
-                  string.pred = " ",
-                  string.intercept = "Intercept",
-                  pred.labels = predictor_labels,#,
-                  dv.labels = rep(c("Exit intention"),each=4),
-                  #dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2),
-                  order.terms = c(2,5:6,3:4,1))
-
-```
-
-```{r}
-voice_mod1 <- exit_mod1 %>% update(PROJECT_VOICE~.+ PAST_VOICE)
-voice_mod2 <- voice_mod1 %>%  update(.~. + PROJECT_POLITICIZATION)
-voice_mod3 <- voice_mod1 %>%  update(.~. + PROJECT_INFLUENCE)
-voice_mod4 <- voice_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
-
-sjPlot::tab_model(voice_mod1,voice_mod2,voice_mod3,voice_mod4,
-                  show.ci = F,
-                  show.se = T,
-                  show.std = T,
-                  collapse.se = T,
-                  emph.p=F,
-                  string.est = "B",
-                  string.std = "Beta",
-                  string.pred = " ",
-                  string.intercept = "Intercept",
-                  pred.labels = predictor_labels,
-                  dv.labels = rep(c("Voice intention"),each=4),
-                  #dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2),
-                  order.terms = c(2,6:7,3:5,1))
-
-```
-
-```{r}
-work_mod1 <- exit_mod1 %>% update(PROJECT_EFFORT~.+ PAST_EFFORT)
-work_mod2 <- work_mod1 %>%  update(.~. + PROJECT_POLITICIZATION)
-work_mod3 <- work_mod1 %>%  update(.~. + PROJECT_INFLUENCE)
-work_mod4 <- work_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
-
-sjPlot::tab_model(work_mod1,work_mod2,work_mod3,work_mod4,
-                  show.ci = F,
-                  show.se = T,
-                  show.std = T,
-                  collapse.se = T,
-                  emph.p=F,
-                  string.est = "B",
-                  string.std = "Beta",
-                  string.pred = " ",
-                  string.intercept = "Intercept",
-                  pred.labels = predictor_labels,
-                  dv.labels = rep(c("Work effort intention"),each=4),
-                  #dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2),
-                  order.terms = c(2,6:7,3:5,1))
-
-```

### 2024-12-05 code/Operationalization.R
Update Operationalization.R
I added ministry by the minister's party affliation

@@ -28,7 +28,7 @@ library(lavaan)
 library(labelled)
 
 #read data with qualtRics 
-setwd("C:\\Users\\Nir\\Dropbox\\Civil Servants' Perceptions of Democratic Decline\\data\\raw data")
+setwd("C:\\Users\\nirko\\Dropbox\\Civil Servants' Perceptions of Democratic Decline\\data\\raw data")
 data <- read_spss("survey_14.3.2023.sav")
 
 #create a new dataset with combined variables for men and women
@@ -307,7 +307,7 @@ new_data$tenure <- as.factor(new_data$tenure)
 levels(new_data$tenure) <- c("1-", "1-5", "6-10", "11-20", "20+")
 
 #ministry
-ministry_text_to_fill <- read.xlsx("C:\\Users\\Nir\\Dropbox\\Civil Servants' Perceptions of Democratic Decline\\data\\coding of units\\units_manually_coded.xlsx")
+ministry_text_to_fill <- read.xlsx("C:\\Users\\nirko\\Dropbox\\Civil Servants' Perceptions of Democratic Decline\\data\\coding of units\\units_manually_coded.xlsx")
 new_data$ministry <- coalesce(new_data$Q31, new_data$Q32)
 
 for (response_id_new_data in 1:length(new_data$ResponseId)){
@@ -319,7 +319,7 @@ for (response_id_new_data in 1:length(new_data$ResponseId)){
 }
 
 #education field
-education_field_to_fill <- read.xlsx("C:\\Users\\Nir\\Dropbox\\Civil Servants' Perceptions of Democratic Decline\\data\\coding of academic degree\\coding_Orpaz.xlsx")
+education_field_to_fill <- read.xlsx("C:\\Users\\nirko\\Dropbox\\Civil Servants' Perceptions of Democratic Decline\\data\\coding of academic degree\\coding_Orpaz.xlsx")
 new_data$education_field <- new_data$Q43
 
 for (response_id_new_data in 1:length(new_data$ResponseId)){
@@ -344,6 +344,42 @@ for (response_id_new_data in 1:length(new_data$ResponseId)){
 #ministry affliation
 new_data$ministry <- as.factor(new_data$ministry)
[…]

### 2024-12-05 code/Weights.R
Add files via upload

@@ -1,0 +1,80 @@
+#import data
+source("C:\\Users\\nirko\\Dropbox\\Civil Servants' Perceptions of Democratic Decline\\Code\\Operationalization & CFA\\Operationalization.R")
+
+## Filter sample data
+filtered_sample_data <- data_for_analysis_extended[data_for_analysis_extended$ranking %in% c("middle", "senior", "very senior"), ]
+
+
+##1. Calculate Population Proportions
+pop_statistics <- readRDS("C:\\Users\\nirko\\Dropbox\\Civil Servants' Perceptions of Democratic Decline\\Code\\Operationalization & CFA\\pop_statistics.rds")
+pop_gender <- pop_statistics$gender_proportions
+pop_age <- pop_statistics$age_proportions
+pop_ranking <- pop_statistics$ranking_proportions
+pop_tenure <- pop_statistics$tenure_proportions
+pop_education <- pop_statistics$education_proportions
+pop_education <- pop_education[c("high school", "bachelor", "master", "phd")] # Reorder and rename
+names(pop_education) <- c("high-school", "bachelor", "master", "phd")
+
+
+
+# 2. Calculate sample proportions
+sample_gender <- prop.table(table(filtered_sample_data$gender))
+sample_age <- prop.table(table(filtered_sample_data$age))
+sample_tenure <- prop.table(table(filtered_sample_data$tenure))
+#ranking - process categores first
+filtered_sample_data$ranking_standardized <- ifelse(
+  filtered_sample_data$ranking == "middle", "middle", "senior_or_very_senior"
+)
+sample_ranking <- prop.table(table(filtered_sample_data$ranking_standardized))
+#education - process the categories before
+filtered_sample_data$education_standardized <- ifelse(
+  filtered_sample_data$education %in% c("high-school", "other"), "high-school",
+  as.character(filtered_sample_data$education) # Retain other categories as they are
+)
+
+filtered_sample_data$education_standardized <- factor(
+  filtered_sample_data$education_standardized,
+  levels = c("high-school", "bachelor", "master", "phd") # Ensure all levels are included
+)
+
+sample_education <- prop.table(table(filtered_sample_data$education_standardized))
+
+# 3. Create weights
+# Gender Weight
+weight_gender <- pop_gender / sample_gender
+
+# Age Weight
+weight_age <- pop_age / sample_age
+
+# Ranking Weight
+weight_ranking <- pop_ranking / sample_ranking
+
+# Tenure Weight
[…]

### 2024-12-05 reports/paper_outputs_Dec_2024.qmd
Update paper_outputs_Dec_2024.qmd

@@
 ```{r}
-#source("Operationalization_31.7.R")
+#source("C:\\Users\\nirko\\Dropbox\\Civil Servants' Perceptions of Democratic Decline\\Code\\Operationalization & CFA\\Operationalization.R")
+#source("C:\\Users\\nirko\\Dropbox\\Civil Servants' Perceptions of Democratic Decline\\Code\\Operationalization & CFA\\Weights.R")
 
@@
 ```{r}
+#filter data
+data_for_analysis_senior <- new_data %>% 
+  filter((ranking !="junior") %>% replace_na(TRUE)) %>% 
+  filter(INTENT_EXIT_2>0|
+           PROJECT_EFFORT>0|
+           PROJECT_VOICE>0)
+
 cfa.model.1factor <-
@@
             data=data_for_analysis_senior)
+exit_mod2 <- exit_mod1 %>%  update(.~. + PROJECT_POLITICIZATION)
+exit_mod3 <- exit_mod1 %>%  update(.~. + PROJECT_INFLUENCE)
+exit_mod4 <- exit_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
+
+sjPlot::tab_model(exit_mod1,exit_mod2,exit_mod3,exit_mod4,
+                  show.ci = F,
+                  show.se = T,
+                  show.std = T,
+                  collapse.se = T,
+                  emph.p=F,
+                  string.est = "B",
+                  string.std = "Beta",
+                  string.pred = " ",
+                  string.intercept = "Intercept",
+                  pred.labels = predictor_labels,#,
+                  dv.labels = rep(c("Exit intention"),each=4),
+                  #dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2),
+                  order.terms = c(2,5:6,3:4,1))
+
+```
+
+```{r}
+voice_mod1 <- exit_mod1 %>% update(PROJECT_VOICE~.+ PAST_VOICE)
+voice_mod2 <- voice_mod1 %>%  update(.~. + PROJECT_POLITICIZATION)
+voice_mod3 <- voice_mod1 %>%  update(.~. + PROJECT_INFLUENCE)
+voice_mod4 <- voice_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
+
+sjPlot::tab_model(voice_mod1,voice_mod2,voice_mod3,voice_mod4,
+                  show.ci = F,
+                  show.se = T,
+                  show.std = T,
+                  collapse.se = T,
+                  emph.p=F,
+                  string.est = "B",
+                  string.std = "Beta",
+                  string.pred = " ",
+                  string.intercept = "Intercept",
+                  pred.labels = predictor_labels,
+                  dv.labels = rep(c("Voice intention"),each=4),
+                  #dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2),
+                  order.terms = c(2,6:7,3:5,1))
+
+```
+
+```{r}
+work_mod1 <- exit_mod1 %>% update(PROJECT_EFFORT~.+ PAST_EFFORT)
+work_mod2 <- work_mod1 %>%  update(.~. + PROJECT_POLITICIZATION)
+work_mod3 <- work_mod1 %>%  update(.~. + PROJECT_INFLUENCE)
+work_mod4 <- work_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
+
+sjPlot::tab_model(work_mod1,work_mod2,work_mod3,work_mod4,
+                  show.ci = F,
+                  show.se = T,
+                  show.std = T,
+                  collapse.se = T,
+                  emph.p=F,
+                  string.est = "B",
+                  string.std = "Beta",
+                  string.pred = " ",
+                  string.intercept = "Intercept",
+                  pred.labels = predictor_labels,
+                  dv.labels = rep(c("Work effort intention"),each=4),
+                  #dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2),
+                  order.terms = c(2,6:7,3:5,1))
+
+```
+
+Model for exit, voice and work - weighted
+```{r}
+
+# Merge the dataset with weights with the data_for_analysis_senior based on ResponseId and add the combined_weight column
+data_for_analysis_senior <- merge(data_for_analysis_senior, 
+                                   data_for_analysis_with_weights[, c("ResponseId", "combined_weight")], 
+                                   by = "ResponseId", 
+                                   all.x = TRUE)
+
+# standardize weight
+data_for_analysis_senior$standardized_weight <- as.numeric(data_for_analysis_senior$combined_weight / mean(data_for_analysis_senior$combined_weight, na.rm = TRUE))
+
+exit_mod1 <- lm(INTENT_EXIT_2 ~ 
+            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
+            data=data_for_analysis_senior,
+            weights = standardized_weight)
 exit_mod2 <- exit_mod1 %>%  update(.~. + PROJECT_POLITICIZATION)

### 2024-12-06 reports/paper_outputs_Dec_2024.qmd
Update paper_outputs_Dec_2024.qmd

--- 2024-12-02 reports/paper_outputs_Dec_2024.qmd
@@
 
-exit_mod3 <- exit_mod1 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)
+exit_mod3 <- exit_mod1 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)
 
-exit_mod4 <- exit_mod2 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)
+exit_mod4 <- exit_mod2 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)
 
@@
 politicization_mod1 <- lm(PROJECT_POLITICIZATION ~ 
-            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist,
+            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party,
             data=data_for_analysis_senior)
@@
             BACKSLIDING_2 +   
-              PAST_POLITICIZATION + PAST_INFLUENCE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist,
+              PAST_POLITICIZATION + PAST_INFLUENCE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party,
             data=data_for_analysis_senior)
@@
 
-voice_mod1 <- exit_mod1 %>% update(PROJECT_VOICE~.+ PAST_VOICE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)
+voice_mod1 <- exit_mod1 %>% update(PROJECT_VOICE~.+ PAST_VOICE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist + ministry_by_party)
 voice_mod1_relig <- voice_mod1 %>% update(.~.+religiosity)
 
-work_mod1 <- exit_mod1 %>% update(PROJECT_EFFORT~.+ PAST_EFFORT+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)
+work_mod1 <- exit_mod1 %>% update(PROJECT_EFFORT~.+ PAST_EFFORT+ education+ gender +tenure+ position_type+ ranking+ age+ jurist + ministry_by_party)
 work_mod1_relig <- work_mod1 %>% update(.~.+religiosity)

### 2024-12-06 reports/paper_outputs_Dec_2024.qmd
Update SEM models

--- 2024-12-02 reports/paper_outputs_Dec_2024.qmd
@@
 sjPlot::tab_model(politicization_mod1,influence_mod1,
+                  show.est = F,
                   show.ci = F,
-                  show.se = T,
+                  show.se = F,
                   show.std = T,
@@
                   work_mod1,work_mod2,
+                  show.est = F,
                   show.ci = F,
@@
 SEM_All <-'
+##latent variables##
+Past_influence=~ Q4_1 + Q4_2 + Q4_3
+Past_politicization=~ Q10_1 + Q10_2 + Q10_3
+Demo_backsliding=~ Q16_1 + Q16_2 + Q16_3 + Q16_4 + Q16_5 + Q15
+Past_voice=~Q22_1+Q22_2+Q22_3
+Past_effort=~PAST_EFFORT
 
 ##Direct effects##
-INTENT_EXIT_2 ~ cp_ex*BACKSLIDING_2
-PROJECT_VOICE ~ cp_vc*BACKSLIDING_2 + PAST_VOICE
-PROJECT_EFFORT ~ cp_eff*BACKSLIDING_2 + PAST_EFFORT
+INTENT_EXIT_2 ~ cp_ex*Demo_backsliding
+PROJECT_VOICE ~ cp_vc*Demo_backsliding + Past_voice
+PROJECT_EFFORT ~ cp_eff*Demo_backsliding + Past_effort
 
 ##Mediators##
-PROJECT_POLITICIZATION ~ a1*BACKSLIDING_2 + PAST_POLITICIZATION 
-PROJECT_INFLUENCE ~ a2*BACKSLIDING_2 + PAST_INFLUENCE
+PROJECT_POLITICIZATION ~ a1*Demo_backsliding + Past_politicization 
+PROJECT_INFLUENCE ~ a2*Demo_backsliding + Past_influence
 
-INTENT_EXIT_2 ~ b1_ex*PROJECT_POLITICIZATION + PAST_POLITICIZATION
-INTENT_EXIT_2 ~ b2_ex*PROJECT_INFLUENCE + PAST_INFLUENCE
+INTENT_EXIT_2 ~ b1_ex*PROJECT_POLITICIZATION + Past_politicization
+INTENT_EXIT_2 ~ b2_ex*PROJECT_INFLUENCE + Past_influence
 
-PROJECT_VOICE ~ b1_vc*PROJECT_POLITICIZATION + PAST_POLITICIZATION
-PROJECT_VOICE ~ b2_vc*PROJECT_INFLUENCE + PAST_INFLUENCE
+PROJECT_VOICE ~ b1_vc*PROJECT_POLITICIZATION + Past_politicization
+PROJECT_VOICE ~ b2_vc*PROJECT_INFLUENCE + Past_influence
 
-PROJECT_EFFORT ~ b1_eff*PROJECT_POLITICIZATION + PAST_POLITICIZATION
-PROJECT_EFFORT ~ b2_eff*PROJECT_INFLUENCE + PAST_INFLUENCE
+PROJECT_EFFORT ~ b1_eff*PROJECT_POLITICIZATION + Past_politicization
+PROJECT_EFFORT ~ b2_eff*PROJECT_INFLUENCE + Past_influence
 
@@
 ##Other correlations##
-PROJECT_POLITICIZATION~~PAST_INFLUENCE
-PROJECT_INFLUENCE~~PAST_POLITICIZATION
-PAST_POLITICIZATION~~PAST_INFLUENCE
-PAST_EFFORT~~PROJECT_POLITICIZATION
-PAST_EFFORT~~PROJECT_INFLUENCE
+PROJECT_POLITICIZATION~~Past_influence
+PROJECT_INFLUENCE~~Past_politicization
+Past_politicization~~Past_influence
+Past_effort~~PROJECT_POLITICIZATION
+Past_effort~~PROJECT_INFLUENCE
 
@@
 ```{r}
+standardizedSolution_boot_ci(fit_all) %>% 
+  #filter(op==":=") %>% 
+  dplyr::select(label,est.std,boot.ci.lower,boot.ci.upper,pvalue) %>% 
+  mutate(across(2:4, round, 2)) %>% 
+  mutate(across(5, round, 3)) %>% 
+  gt::gt()
+```
+
+```{r}
 parameterEstimates(fit_all, boot.ci.type	="basic", standardized = T, output = "text")
+```
+
+```{r}
+fitmeasures(fit_all, c('chisq','df','pvalue','cfi','tli', 'rmsea', 'rmsea.ci.upper','rmsea.ci.lower', 'srmr')) %>% 
+  broom::tidy() %>% 
+  pivot_wider(names_from = names,values_from = x) %>% 
+  mutate(chisq_01 = str_c(chisq %>% round(3)," [","df=",df,", p=",pvalue %>% round(3),"]"),
+         rmsea_01 = str_c(rmsea %>% round(3)," CI[", rmsea.ci.lower %>% round(3),",",rmsea.ci.upper %>% round(3),"]"),
+         cfi = cfi %>% round(3),
+         tli = tli %>% round(3),
+         srmr = srmr %>% round(3),
+         n = fit_all@SampleStats@nobs) %>%
+  dplyr::select('N' = n,
+          'Chi-sq' = chisq_01,
+         'CFI' = cfi,
+         'TLI' = tli,
+         'RMSEA' = rmsea_01,
+         'SRMR' = srmr) %>% 
+  t() %>% 
+  kableExtra::kable()
 ```
@@
 ```
+
+```{r, fig.width=8,fig.height=6}
+p1<- cars %>% ggplot(aes(x=speed))+ geom_histogram()
+
+p1
+
+#ggsave("p1.jpg",width = 8, height = 4,dpi=600)
+```

### 2024-12-08 reports/paper_outputs_Dec_2024.qmd
clean code

@@
 
-Model for exit, voice and work
-```{r}
-exit_mod1 <- lm(INTENT_EXIT_2 ~ 
-            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
-            data=data_for_analysis_senior)
-exit_mod2 <- exit_mod1 %>%  update(.~. + PROJECT_POLITICIZATION)
-exit_mod3 <- exit_mod1 %>%  update(.~. + PROJECT_INFLUENCE)
-exit_mod4 <- exit_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
-
-sjPlot::tab_model(exit_mod1,exit_mod2,exit_mod3,exit_mod4,
-                  show.ci = F,
-                  show.se = T,
-                  show.std = T,
-                  collapse.se = T,
-                  emph.p=F,
-                  string.est = "B",
-                  string.std = "Beta",
-                  string.pred = " ",
-                  string.intercept = "Intercept",
-                  pred.labels = predictor_labels,#,
-                  dv.labels = rep(c("Exit intention"),each=4),
-                  #dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2),
-                  order.terms = c(2,5:6,3:4,1))
-
-```
-
-```{r}
-voice_mod1 <- exit_mod1 %>% update(PROJECT_VOICE~.+ PAST_VOICE)
-voice_mod2 <- voice_mod1 %>%  update(.~. + PROJECT_POLITICIZATION)
-voice_mod3 <- voice_mod1 %>%  update(.~. + PROJECT_INFLUENCE)
-voice_mod4 <- voice_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
-
-sjPlot::tab_model(voice_mod1,voice_mod2,voice_mod3,voice_mod4,
-                  show.ci = F,
-                  show.se = T,
-                  show.std = T,
-                  collapse.se = T,
-                  emph.p=F,
-                  string.est = "B",
-                  string.std = "Beta",
-                  string.pred = " ",
-                  string.intercept = "Intercept",
-                  pred.labels = predictor_labels,
-                  dv.labels = rep(c("Voice intention"),each=4),
-                  #dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2),
-                  order.terms = c(2,6:7,3:5,1))
-
-```
-
-```{r}
-work_mod1 <- exit_mod1 %>% update(PROJECT_EFFORT~.+ PAST_EFFORT)
-work_mod2 <- work_mod1 %>%  update(.~. + PROJECT_POLITICIZATION)
-work_mod3 <- work_mod1 %>%  update(.~. + PROJECT_INFLUENCE)
-work_mod4 <- work_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
-
-sjPlot::tab_model(work_mod1,work_mod2,work_mod3,work_mod4,
-                  show.ci = F,
-                  show.se = T,
-                  show.std = T,
-                  collapse.se = T,
-                  emph.p=F,
-                  string.est = "B",
-                  string.std = "Beta",
-                  string.pred = " ",
-                  string.intercept = "Intercept",
-                  pred.labels = predictor_labels,
-                  dv.labels = rep(c("Work effort intention"),each=4),
-                  #dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2),
-                  order.terms = c(2,6:7,3:5,1))
-
-```
-
 ## SEM models
@@
 standardizedSolution_boot_ci(fit_all) %>% 
-  #filter(op==":=") %>% 
+  filter(op==":=") %>% 
   dplyr::select(label,est.std,boot.ci.lower,boot.ci.upper,pvalue) %>% 

### 2024-12-08 reports/paper_outputs_Dec_2024.qmd
Update paper_outputs_Dec_2024.qmd

@@
 
+```{r}
+#regression outputs with CIs
+sjPlot::tab_model(politicization_mod1,influence_mod1,
+                  show.std=T
+)
+```
+
 Model for exit, voice and work
@@
 ```{r}
+#regression outputs with CIs
 sjPlot::tab_model(exit_mod1,exit_mod2,
                   voice_mod1,voice_mod2,
-                  work_mod1,work_mod2)
+                  work_mod1,work_mod2,
+                  show.std=T
+)
 ```

### 2024-12-20 reports/paper_outputs_Dec_2024.qmd
Update paper_outputs_Dec_2024.qmd

--- 2024-12-08 reports/paper_outputs_Dec_2024.qmd
@@
 
+Alternative Measure for Exit
+
 ```{r}
+
 exit_mod1 <- lm(INTENT_EXIT_1 ~ 
-            BACKSLIDING_2,
-            data=data_for_analysis_senior)
+                  BACKSLIDING_2 + PAST_POLITICIZATION + PAST_INFLUENCE,
+                data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))
 
@@
 
-exit_mod3 <- exit_mod1 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)
+exit_mod3 <- lm(INTENT_EXIT_1 ~ 
+                  BACKSLIDING_2 + PAST_POLITICIZATION + PAST_INFLUENCE + education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party,
+                data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))
 
-exit_mod4 <- exit_mod2 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)
+exit_mod4 <- exit_mod3 %>% update(.~.+ PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
 
-#Table A8
+#Table A12.3
 sjPlot::tab_model(exit_mod1,exit_mod2,
@@
                   show.se = T,
-                  collapse.se = T,
-                  terms = c("(Intercept)",
-                            "BACKSLIDING_2",
-                            "PROJECT_POLITICIZATION",
-                            "PROJECT_INFLUENCE"))
+                  collapse.se = T)
 
@@
 ```{r}
+
 exit_mod1 <- lm(INTENT_EXIT_2 ~ 
-            BACKSLIDING_2,
-            data=data_for_analysis_senior)
+                  BACKSLIDING_2 + PAST_POLITICIZATION + PAST_INFLUENCE,
+                data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))
 
@@
 
-exit_mod3 <- exit_mod1 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)
+exit_mod3 <- lm(INTENT_EXIT_2 ~ 
+                  BACKSLIDING_2 + PAST_POLITICIZATION + PAST_INFLUENCE + education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party,
+                data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))
 
-exit_mod4 <- exit_mod2 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)
+exit_mod4 <- exit_mod3 %>% update(.~.+ PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
 
-#Table A8
+#Table A12.4
 sjPlot::tab_model(exit_mod1,exit_mod2,
@@
 )
+
+#set Other as a base for ministry_by_party
+data_for_analysis_senior$ministry_by_party <- relevel(data_for_analysis_senior$ministry_by_party, ref = "Other")
+#set Very Senior as a based for ranking
+data_for_analysis_senior$ranking <- relevel(data_for_analysis_senior$ranking, ref = "very senior")
+
 ```
@@
 politicization_mod1 <- lm(PROJECT_POLITICIZATION ~ 
-            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist,
+                            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
                           data=data_for_analysis_senior)
-politicization_mod1_relig <- politicization_mod1 %>% update(.~.+religiosity)
+politicization_mod1_controls <- politicization_mod1 %>% update(.~.+religiosity + education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)
+
+sjPlot::tab_model(
+                  politicization_mod1,politicization_mod1_controls,
+                  show.ci = F,
+                  show.se = T,
+                  show.std = T,
+                  collapse.se = T,
+                  emph.p=F,
+                  string.est = "B",
+                  string.std = "Beta",
+                  string.pred = " ",
+                  string.intercept = "Intercept",
+                  pred.labels = predictor_labels)#,
+dv.labels = c("Expected politicization","Expected influence")
 
 influence_mod1 <- politicization_mod1 %>%  update(PROJECT_INFLUENCE~.)
-influence_mod1_relig <- influence_mod1 %>% update(.~.+religiosity)
+influence_mod1_controls <- influence_mod1 %>% update(.~.+religiosity + education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)
 
-sjPlot::tab_model(politicization_mod1,politicization_mod1_relig,
-                  influence_mod1,influence_mod1_relig,
+sjPlot::tab_model(
+                  influence_mod1,influence_mod1_controls,
                   show.ci = F,
@@
 ```{r}
+
 exit_mod1 <- lm(INTENT_EXIT_2 ~ 
-            BACKSLIDING_2 +   
-              PAST_POLITICIZATION + PAST_INFLUENCE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist,
-            data=data_for_analysis_senior)
-exit_mod1_relig <- exit_mod1 %>% update(.~.+religiosity)
+                  BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
+                data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))
 
-voice_mod1 <- exit_mod1 %>% update(PROJECT_VOICE~.+ PAST_VOICE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)
-voice_mod1_relig <- voice_mod1 %>% update(.~.+religiosity)
+exit_mod2 <- exit_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
+exit_mod3 <- exit_mod2 %>%  update(.~. +religiosity + education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)
 
-work_mod1 <- exit_mod1 %>% update(PROJECT_EFFORT~.+ PAST_EFFORT+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)
-work_mod1_relig <- work_mod1 %>% update(.~.+religiosity)
-
-sjPlot::tab_model(exit_mod1,exit_mod1_relig,
-                  voice_mod1,voice_mod1_relig,
-                  work_mod1,work_mod1_relig,
+sjPlot::tab_model(exit_mod1,
+                  exit_mod2,
+                  exit_mod3,
                   show.ci = F,
@@
                   string.intercept = "Intercept",
-                  pred.labels = predictor_labels,
-                  dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2))
+                  pred.labels = predictor_labels)
+
+voice_mod1 <- exit_mod1 %>% update(PROJECT_VOICE~.+ PAST_VOICE)
+voice_mod2 <- voice_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
+voice_mod3 <- voice_mod2 %>%  update(.~. +religiosity + education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)
+
+sjPlot::tab_model(voice_mod1,
+                  voice_mod2,
+                  voice_mod3,
+                  show.ci = F,
+                  show.se = T,
+                  show.std = T,
+                  collapse.se = T,
+                  emph.p=F,
+                  string.est = "B",
+                  string.std = "Beta",
+                  string.pred = " ",
+                  string.intercept = "Intercept",
+                  pred.labels = predictor_labels)
+
+work_mod1 <- exit_mod1 %>% update(PROJECT_EFFORT~.+ PAST_EFFORT)
+work_mod2 <- work_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
+work_mod3 <- work_mod2 %>%  update(.~. +religiosity + education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)
+
+sjPlot::tab_model(work_mod1,
+                  work_mod2,
+                  work_mod3,
+                  show.ci = F,
+                  show.se = T,
+                  show.std = T,
+                  collapse.se = T,
+                  emph.p=F,
+                  string.est = "B",
+                  string.std = "Beta",
+                  string.pred = " ",
+                  string.intercept = "Intercept",
+                  pred.labels = predictor_labels)
 
@@
 
-```{r, fig.width=8,fig.height=6}
-p1<- cars %>% ggplot(aes(x=speed))+ geom_histogram()
+Models with interactions 
+```{r}
 
-p1
+#set Other as a base for ministry_by_party
+data_for_analysis_senior$ministry_by_party <- relevel(data_for_analysis_senior$ministry_by_party, ref = "Other")
+#set very Senior as a based for ranking
+data_for_analysis_senior$ranking <- relevel(data_for_analysis_senior$ranking, ref = "very senior")
 
-#ggsave("p1.jpg",width = 8, height = 4,dpi=600)
+#exit
+exit_mod1 <- lm(INTENT_EXIT_2 ~ 
+                  BACKSLIDING_2 +   
+                  PAST_POLITICIZATION + PAST_INFLUENCE+ PROJECT_POLITICIZATION + PROJECT_INFLUENCE +education+ gender +tenure+ position_type+ ranking+ age+ jurist + ministry_by_party,
+                data=data_for_analysis_senior)
+exit_mod1_ministry_by_party_interaction <- exit_mod1 %>% update(.~.+ BACKSLIDING_2:ministry_by_party )
+exit_mod1_jurist_interaction <- exit_mod1 %>% update(.~.+ BACKSLIDING_2:jurist )
+
+sjPlot::tab_model(exit_mod1,exit_mod1_ministry_by_party_interaction,exit_mod1_jurist_interaction,
+                  show.ci = F,
+                  show.se = T,
+                  show.std = T,
+                  collapse.se = T,
+                  emph.p=F,
+                  string.est = "B",
+                  string.std = "Beta",
+                  string.pred = " ",
+                  string.intercept = "Intercept",
+                  pred.labels = predictor_labels)
+
+#voice
+
+voice_mod1 <- lm(PROJECT_VOICE ~ 
+                  BACKSLIDING_2 +   
+                  PAST_POLITICIZATION + PAST_INFLUENCE+ PROJECT_POLITICIZATION + PROJECT_INFLUENCE +education+ gender +tenure+ position_type+ ranking+ age+ jurist + ministry_by_party,
+                data=data_for_analysis_senior)
+voice_mod1_ministry_by_party_interaction <- voice_mod1 %>% update(.~.+ BACKSLIDING_2:ministry_by_party )
+voice_mod1_jurist_interaction <- voice_mod1 %>% update(.~.+ BACKSLIDING_2:jurist )
+
+sjPlot::tab_model(voice_mod1,voice_mod1_ministry_by_party_interaction,voice_mod1_jurist_interaction,
+                  show.ci = F,
+                  show.se = T,
+                  show.std = T,
+                  collapse.se = T,
+                  emph.p=F,
+                  string.est = "B",
+                  string.std = "Beta",
+                  string.pred = " ",
+                  string.intercept = "Intercept",
+                  pred.labels = predictor_labels)
+
+#EFFORT
+
+effort_mod1 <- lm(PROJECT_EFFORT ~ 
+                   BACKSLIDING_2 +   
+                   PAST_POLITICIZATION + PAST_INFLUENCE+ PROJECT_POLITICIZATION + PROJECT_INFLUENCE +education+ gender +tenure+ position_type+ ranking+ age+ jurist + ministry_by_party,
+                 data=data_for_analysis_senior)
+effort_mod1_ministry_by_party_interaction <- effort_mod1 %>% update(.~.+ BACKSLIDING_2:ministry_by_party )
+effort_mod1_jurist_interaction <- effort_mod1 %>% update(.~.+ BACKSLIDING_2:jurist )
+
+sjPlot::tab_model(effort_mod1,effort_mod1_ministry_by_party_interaction,effort_mod1_jurist_interaction,
+                  show.ci = F,
+                  show.se = T,
+                  show.std = T,
+                  collapse.se = T,
+                  emph.p=F,
+                  string.est = "B",
+                  string.std = "Beta",
+                  string.pred = " ",
+                  string.intercept = "Intercept",
+                  pred.labels = predictor_labels)
+
 ```

### 2024-12-20 code/Weights.R
Update Weights.R

@@ -2,7 +2,7 @@
 source("C:\\Users\\nirko\\Dropbox\\Civil Servants' Perceptions of Democratic Decline\\Code\\Operationalization & CFA\\Operationalization.R")
 
 ## Filter sample data
-filtered_sample_data <- data_for_analysis_extended[data_for_analysis_extended$ranking %in% c("middle", "senior", "very senior"), ]
+filtered_sample_data <- data_for_analysis_senior[data_for_analysis_senior$ranking %in% c("middle", "senior", "very senior"), ]
 
 
 ##1. Calculate Population Proportions
@@ -73,8 +73,83 @@ filtered_sample_data$weight_education <- weight_education[match(filtered_sample_
 
 # 5. Combine Weights
 # Combine weights for each observation
-filtered_sample_data$combined_weight <- with(filtered_sample_data,
+filtered_sample_data$combined_weights <- with(filtered_sample_data,
                                              weight_gender * weight_age * weight_ranking * weight_tenure * weight_education)
 
 data_for_analysis_with_weights <- filtered_sample_data
+
+# 6. Run models with weights 
+# Merge the 'combined_weights' column from 'filtered_sample_data' into 'data_for_analysis_senior'
+data_for_analysis_senior <- merge(
+  data_for_analysis_senior,
+  data_for_analysis_with_weights[, c("ResponseId", "combined_weights")],
+  by = "ResponseId",
+  all.x = TRUE
+)
+
+data_for_analysis_senior <- data_for_analysis_senior[!is.na(data_for_analysis_senior$combined_weight), ]
+data_for_analysis_senior$combined_weights <- as.numeric(as.character(data_for_analysis_senior$combined_weights)) 
+
+
+#exit
+exit_mod1 <- lm(INTENT_EXIT_2 ~ 
+                  BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
+                data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))
+
+exit_mod2 <- exit_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
+exit_mod3 <- exit_mod2 %>%  update(.~. + combined_weights)
+
+sjPlot::tab_model(exit_mod1,
+                  exit_mod2,
+                  exit_mod3,
+                  show.ci = F,
+                  show.se = T,
+                  show.std = T,
+                  collapse.se = T,
+                  emph.p=F,
[…]

### 2024-12-22 reports/paper_outputs_Dec_2024.qmd
Update paper_outputs_Dec_2024.qmd

@@
 Alternative Measure for Exit 
-
 ```{r}
@@
 
-```
-
-```{r}
-
 exit_mod1 <- lm(INTENT_EXIT_2 ~ 
@@
 ```
-
-## Controls
 
@@
 ```
+
+Models with Junior Civil Servants
+```{r}
+
+## include junior
+data_for_analysis_all <- new_data %>% 
+  filter(INTENT_EXIT_2>0|
+           PROJECT_EFFORT>0|
+           PROJECT_VOICE>0)
+
+exit_mod1 <- lm(INTENT_EXIT_2 ~ 
+                  BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
+                data=data_for_analysis_all %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))
+
+exit_mod2 <- exit_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
+
+voice_mod1 <- exit_mod1 %>% update(PROJECT_VOICE~.+ PAST_VOICE)
+voice_mod2 <- voice_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
+
+work_mod1 <- exit_mod1 %>% update(PROJECT_EFFORT~.+ PAST_EFFORT)
+work_mod2 <- work_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
+
+sjPlot::tab_model(exit_mod1,exit_mod2,
+                  voice_mod1,voice_mod2,
+                  work_mod1,work_mod2,
+                  show.est = F,
+                  show.ci = F,
+                  show.se = T,
+                  show.std = T,
+                  collapse.se = T,
+                  emph.p=F,
+                  string.est = "B",
+                  string.std = "Beta",
+                  string.pred = " ",
+                  string.intercept = "Intercept",
+                  pred.labels = predictor_labels,
+                  dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2),
+                  order.terms = c(2,5:6,3:4,7:8,1))
+
+```
+
+```{r, fig.width=8,fig.height=6}
+p1<- cars %>% ggplot(aes(x=speed))+ geom_histogram()
+
+p1
+
+#ggsave("p1.jpg",width = 8, height = 4,dpi=600)
+```

### 2024-12-23 code/Operationalization_with_weights.R
delete old weight files

@@ -1,521 +1,0 @@
-########################
-#title: "Operationalization"
-#author: "Nir Kosti"
-#date: "`r Sys.time()`"
-########################
-
-
-# hebrew setup
-Sys.setlocale(category = "LC_ALL", locale = "Hebrew_Israel.1255")
-#rmarkdown setup
-knitr::opts_chunk$set(message = FALSE)
-#read relevant libraries 
-library(haven)
-library(scales)
-library(ggplot2)
-library(reshape2)
-library(ggthemes)
-library(dplyr)
-library(qualtRics)
-library(tidyr)
-library(stringr)
-library(gridExtra)
-library(openxlsx)
-library(scales)
-#library(gtsummary)
-library(psy)
-library(lavaan)
-library(labelled)
-
-#read data with qualtRics 
-setwd("C:\\Users\\nirko\\Dropbox\\Civil Servants' Perceptions of Democratic Decline\\data\\raw data")
-data <- read_spss("survey_14.3.2023.sav")
-
-#create a new dataset with combined variables for men and women
-new_data <- data[, 1:19]
-
-#combine variables for men and women
-new_data$Q2 <- coalesce(data$Q2_cs_filter, data$Q2_f)
-
-#Q4 - influence past
-new_data$Q4_1 <- coalesce(data$Q4_influence_past_1, data$Q4_f_influence_past_1)
-new_data$Q4_2 <- coalesce(data$Q4_influence_past_2, data$Q4_f_influence_past_2)
-new_data$Q4_3 <-coalesce(data$Q4_influence_past_3, data$Q4_f_influence_past_3)
-
-#Q5 - influence future
-new_data$Q5 <- coalesce(data$Q5_influence_future, data$Q5_f_influence_futur)
-
-#Q6 - influence comments
-new_data$Q6 <- str_c(data$Q6_influence_comment, data$Q6_f_influence_comme)
-
-#Q10 - meritocracy - past
-new_data$Q10_1 <- coalesce(data$Q10_meritocracy_past_1, data$Q10_f_meritocracy_pa_1)
-new_data$Q10_2 <- coalesce(data$Q10_meritocracy_past_2, data$Q10_f_meritocracy_pa_2)
[…]

### 2024-12-23 code/Weights.R

@@ -1,80 +1,0 @@
-#import data
-source("C:\\Users\\nirko\\Dropbox\\Civil Servants' Perceptions of Democratic Decline\\Code\\Operationalization & CFA\\Operationalization.R")
-
-## Filter sample data
-filtered_sample_data <- data_for_analysis_extended[data_for_analysis_extended$ranking %in% c("middle", "senior", "very senior"), ]
-
-
-##1. Calculate Population Proportions
-pop_statistics <- readRDS("C:\\Users\\nirko\\Dropbox\\Civil Servants' Perceptions of Democratic Decline\\Code\\Operationalization & CFA\\pop_statistics.rds")
-pop_gender <- pop_statistics$gender_proportions
-pop_age <- pop_statistics$age_proportions
-pop_ranking <- pop_statistics$ranking_proportions
-pop_tenure <- pop_statistics$tenure_proportions
-pop_education <- pop_statistics$education_proportions
-pop_education <- pop_education[c("high school", "bachelor", "master", "phd")] # Reorder and rename
-names(pop_education) <- c("high-school", "bachelor", "master", "phd")
-
-
-
-# 2. Calculate sample proportions
-sample_gender <- prop.table(table(filtered_sample_data$gender))
-sample_age <- prop.table(table(filtered_sample_data$age))
-sample_tenure <- prop.table(table(filtered_sample_data$tenure))
-#ranking - process categores first
-filtered_sample_data$ranking_standardized <- ifelse(
-  filtered_sample_data$ranking == "middle", "middle", "senior_or_very_senior"
-)
-sample_ranking <- prop.table(table(filtered_sample_data$ranking_standardized))
-#education - process the categories before
-filtered_sample_data$education_standardized <- ifelse(
-  filtered_sample_data$education %in% c("high-school", "other"), "high-school",
-  as.character(filtered_sample_data$education) # Retain other categories as they are
-)
-
-filtered_sample_data$education_standardized <- factor(
-  filtered_sample_data$education_standardized,
-  levels = c("high-school", "bachelor", "master", "phd") # Ensure all levels are included
-)
-
-sample_education <- prop.table(table(filtered_sample_data$education_standardized))
-
-# 3. Create weights
-# Gender Weight
-weight_gender <- pop_gender / sample_gender
-
-# Age Weight
-weight_age <- pop_age / sample_age
-
-# Ranking Weight
-weight_ranking <- pop_ranking / sample_ranking
-
-# Tenure Weight
[…]

### 2024-12-23 reports/paper_outputs_Dec_2024.qmd
Update paper_outputs_Dec_2024.qmd

--- 2024-12-09 reports/paper_outputs_Dec_2024.qmd
@@
 
+data_for_analysis_senior <- data_for_analysis_extended %>% 
+  filter((ranking !="junior") %>% replace_na(TRUE)) %>% 
+  filter(INTENT_EXIT_2>0|
+          PROJECT_EFFORT>0|
+           PROJECT_VOICE>0)
 ```
@@
   gtsummary::tbl_summary()
+
 ```
@@
 
-# Online appendix
-
-## Causal mediation analysis
-
-Exit
-
-```{r}
-# Load necessary package
-library(mediation)
-set.seed(2023)
-
-t1 <- data_for_analysis_senior %>% 
-  drop_na(BACKSLIDING_2,INTENT_EXIT_2,PROJECT_VOICE,PROJECT_EFFORT,PROJECT_POLITICIZATION,PROJECT_INFLUENCE)
-
-# Mediator 1 model
-med1_model <- lm(PROJECT_POLITICIZATION ~ 
-            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
-            data=t1)
-
-# Mediator 2 model
-med2_model <- lm(PROJECT_INFLUENCE ~ 
-            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
-            data=t1)
-
-# Outcome model med 1
-outcome_model_1 <-
-  lm(INTENT_EXIT_2 ~ 
-            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE +
-            PROJECT_POLITICIZATION,
-            data=t1)
-
-# Outcome model med 2
-outcome_model_2 <-
-  lm(INTENT_EXIT_2 ~ 
-            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE +
-            PROJECT_INFLUENCE,
-            data=t1)
-
-# Mediation analysis for the first mediator with bootstrapping
-mediation_result_exit_politicization <-
-  mediate(
-    med1_model,
-    outcome_model_1,
-    treat = "BACKSLIDING_2",
-    mediator = "PROJECT_POLITICIZATION",
-    boot = TRUE,
-    sims = 1000
-  )
-
-# Mediation analysis for the second mediator with bootstrapping
-mediation_result_exit_influence <-
-  mediate(
-    med2_model,
-    outcome_model_2,
-    treat = "BACKSLIDING_2",
-    mediator = "PROJECT_INFLUENCE",
-    boot = TRUE,
-    sims = 1000
-  )
-
-# Summary of the results
-```
-
-```{r}
-summary(mediation_result_exit_politicization) 
-```
-
-```{r}
-summary(mediation_result_exit_influence)
-```
-
-Voice
-
-```{r}
-
-# Outcome model med 1
-outcome_model_1 <-
-  lm(PROJECT_VOICE ~ 
-            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE +
-            PROJECT_POLITICIZATION,
-            data=t1)
-
-# Outcome model med 2
-outcome_model_2 <-
-  lm(PROJECT_VOICE ~ 
-            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE +
-            PROJECT_INFLUENCE,
-            data=t1)
-
-# Mediation analysis for the first mediator with bootstrapping
-mediation_result_voice_politicization <-
-  mediate(
-    med1_model,
-    outcome_model_1,
-    treat = "BACKSLIDING_2",
-    mediator = "PROJECT_POLITICIZATION",
-    boot = TRUE,
-    sims = 1000
-  )
-
-# Mediation analysis for the second mediator with bootstrapping
-mediation_result_voice_influence <-
-  mediate(
-    med2_model,
-    outcome_model_2,
-    treat = "BACKSLIDING_2",
-    mediator = "PROJECT_INFLUENCE",
-    boot = TRUE,
-    sims = 1000
-  )
-
-# Summary of the results
-```
-
-```{r}
-summary(mediation_result_voice_politicization)
-```
-
-```{r}
-summary(mediation_result_voice_influence)
-```
-
-Effort
-
-```{r}
-
-# Outcome model med 1
-outcome_model_1 <-
-  lm(PROJECT_EFFORT ~ 
-            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE + PAST_EFFORT + 
-            PROJECT_POLITICIZATION,
-            data=t1)
-
-# Outcome model med 2
-outcome_model_2 <-
-  lm(PROJECT_EFFORT ~ 
-            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE + PAST_EFFORT + 
-            PROJECT_INFLUENCE,
-            data=t1)
-
-# Mediation analysis for the first mediator with bootstrapping
-mediation_result_work_politicization <-
-  mediate(
-    med1_model,
-    outcome_model_1,
-    treat = "BACKSLIDING_2",
-    mediator = "PROJECT_POLITICIZATION",
-    boot = TRUE,
-    sims = 1000
-  )
-
-# Mediation analysis for the second mediator with bootstrapping
-mediation_result_work_influence <-
-  mediate(
-    med2_model,
-    outcome_model_2,
-    treat = "BACKSLIDING_2",
-    mediator = "PROJECT_INFLUENCE",
-    boot = TRUE,
-    sims = 1000
-  )
-
-# Summary of the results
-```
-
-```{r}
-summary(mediation_result_work_politicization)
-```
-
-```{r}
-summary(mediation_result_work_influence)
-```
-
 ## Descripive illustration
@@
 
-## Exit 1
+# Online appendix
+
+## Exit 1 (online appendix A12)
 
@@
 
+Alternative Measure for Exit 
 ```{r}
+
 exit_mod1 <- lm(INTENT_EXIT_1 ~ 
-            BACKSLIDING_2,
-            data=data_for_analysis_senior)
+                  BACKSLIDING_2 + PAST_POLITICIZATION + PAST_INFLUENCE,
+                data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))
 
@@
 
-exit_mod3 <- exit_mod1 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)
+exit_mod3 <- lm(INTENT_EXIT_1 ~ 
+                  BACKSLIDING_2 + PAST_POLITICIZATION + PAST_INFLUENCE + education+ gender +tenure+ position_type+ ranking+ age+ jurist,
+                data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))
 
-exit_mod4 <- exit_mod2 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)
+exit_mod4 <- exit_mod3 %>% update(.~.+ PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
 
-#Table A8
+#Table A12.3
 sjPlot::tab_model(exit_mod1,exit_mod2,
                   exit_mod3,exit_mod4,
+                  show.est = F,
                   show.ci = F,
-                  show.se = T,
+                  show.se = F,
+                  show.std = T,
                   collapse.se = T,
-                  terms = c("(Intercept)",
-                            "BACKSLIDING_2",
-                            "PROJECT_POLITICIZATION",
-                            "PROJECT_INFLUENCE"))
+                  emph.p=F,
+                  string.est = "B",
+                  string.std = "Beta",
+                  string.pred = " ",
+                  string.intercept = "Intercept",
+                  pred.labels = predictor_labels,
+                  dv.labels = rep(c("exit intention (first measure)"),each=4))
 
@@
 
-```{r}
-exit_mod1 <- lm(INTENT_EXIT_2 ~ 
-            BACKSLIDING_2,
-            data=data_for_analysis_senior)
-
-exit_mod2 <- exit_mod1 %>% update(.~.+ PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
-
-exit_mod3 <- exit_mod1 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)
-
-exit_mod4 <- exit_mod2 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)
-
-#Table A8
-sjPlot::tab_model(exit_mod1,exit_mod2,
-                  exit_mod3,exit_mod4,
-                  show.ci = F,
-                  show.se = T,
-                  collapse.se = T,
-                  terms = c("(Intercept)",
-                            "BACKSLIDING_2",
-                            "PROJECT_POLITICIZATION",
-                            "PROJECT_INFLUENCE"))
-
-```
-
-## Controls
-
-Model for expected politicization & influence
+## Models with controls (online appendix A8)
 
@@
 )
+
+data_for_analysis_senior <- data_for_analysis_senior %>%
+  mutate(ministry_by_party = ministry_by_party %>% as.factor() %>% # Convert to factor
+  relevel(ref = "Likud"), # Set "Other" as reference level
+ranking = ranking %>% relevel(ref = "middle"), #set Very Senior as a based for ranking
+education = education %>% relevel(ref = "bachelor")) #set bachelor as a based for education
+
 ```
@@
 politicization_mod1 <- lm(PROJECT_POLITICIZATION ~ 
-            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party,
+                            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
                           data=data_for_analysis_senior)
-politicization_mod1_relig <- politicization_mod1 %>% update(.~.+religiosity)
+politicization_mod1_controls <- politicization_mod1 %>% update(.~.+religiosity + education+ gender +tenure+ position_type+ ranking+ age+ jurist)
 
 influence_mod1 <- politicization_mod1 %>%  update(PROJECT_INFLUENCE~.)
-influence_mod1_relig <- influence_mod1 %>% update(.~.+religiosity)
+influence_mod1_controls <- influence_mod1 %>% update(.~.+religiosity + education+ gender +tenure+ position_type+ ranking+ age+ jurist)
 
-sjPlot::tab_model(politicization_mod1,politicization_mod1_relig,
-                  influence_mod1,influence_mod1_relig,
+sjPlot::tab_model(
+                  politicization_mod1_controls,influence_mod1_controls,
+                  show.est = F,
                   show.ci = F,
-                  show.se = T,
+                  show.se = F,
                   show.std = T,
@@
                   string.intercept = "Intercept",
-                  pred.labels = predictor_labels)#,
-                  dv.labels = c("Expected politicization","Expected influence")
+                  pred.labels = predictor_labels,
+                  dv.labels = c("Expected politicization","Expected influence"),
+                  order.terms = c(2:4,1))
 
@@
 ```{r}
+#Exit
 exit_mod1 <- lm(INTENT_EXIT_2 ~ 
-            BACKSLIDING_2 +   
-              PAST_POLITICIZATION + PAST_INFLUENCE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party,
-            data=data_for_analysis_senior)
-exit_mod1_relig <- exit_mod1 %>% update(.~.+religiosity)
+                  BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
+                data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))
+exit_mod1_controls <- exit_mod1 %>%  update(.~. +religiosity + education+ gender +tenure+ position_type+ ranking+ age+ jurist)
 
-voice_mod1 <- exit_mod1 %>% update(PROJECT_VOICE~.+ PAST_VOICE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist + ministry_by_party)
-voice_mod1_relig <- voice_mod1 %>% update(.~.+religiosity)
+exit_mod2_controls <- exit_mod1_controls %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
 
-work_mod1 <- exit_mod1 %>% update(PROJECT_EFFORT~.+ PAST_EFFORT+ education+ gender +tenure+ position_type+ ranking+ age+ jurist + ministry_by_party)
-work_mod1_relig <- work_mod1 %>% update(.~.+religiosity)
+#Voice
+voice_mod1 <- lm(PROJECT_VOICE ~ 
+                  BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
+                data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))
+voice_mod1_controls <- voice_mod1 %>%  update(.~. +religiosity + education+ gender +tenure+ position_type+ ranking+ age+ jurist)
 
-sjPlot::tab_model(exit_mod1,exit_mod1_relig,
-                  voice_mod1,voice_mod1_relig,
-                  work_mod1,work_mod1_relig,
+voice_mod2_controls <- voice_mod1_controls %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
+
+#Work
+work_mod1 <- lm(PROJECT_EFFORT ~ 
+                  BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
+                data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))
+work_mod1_controls <- work_mod1 %>%  update(.~. +religiosity + education+ gender +tenure+ position_type+ ranking+ age+ jurist)
+work_mod2_controls <- work_mod1_controls %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
+
+sjPlot::tab_model(exit_mod1_controls,exit_mod2_controls,
+                  voice_mod1_controls,voice_mod2_controls,
+                  work_mod1_controls,work_mod2_controls,
+                  show.est = F,
                   show.ci = F,
@@
 
-```{r, fig.width=8,fig.height=6}
-p1<- cars %>% ggplot(aes(x=speed))+ geom_histogram()
+## Models with Junior Civil Servants (online appendix A8)
 
-p1
+```{r}
 
-#ggsave("p1.jpg",width = 8, height = 4,dpi=600)
+## include junior
+data_for_analysis_all <- new_data %>% 
+  filter(INTENT_EXIT_2>0|
+           PROJECT_EFFORT>0|
+           PROJECT_VOICE>0)
+
 ```
+
+```{r}
+politicization_mod1 <- lm(PROJECT_POLITICIZATION ~ 
+            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
+            data=data_for_analysis_all)
+
+influence_mod1 <- politicization_mod1 %>%  update(PROJECT_INFLUENCE~.)
+
+sjPlot::tab_model(politicization_mod1,influence_mod1,
+                  show.est = F,
+                  show.ci = F,
+                  show.se = F,
+                  show.std = T,
+                  collapse.se = T,
+                  emph.p=F,
+                  string.est = "B",
+                  string.std = "Beta",
+                  string.pred = " ",
+                  string.intercept = "Intercept",
+                  pred.labels = predictor_labels,
+                  dv.labels = c("Expected politicization","Expected influence"),
+                  order.terms = c(2:4,1))
+
+```
+
+```{r}
+exit_mod1 <- lm(INTENT_EXIT_2 ~ 
+                  BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
+                data=data_for_analysis_all %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))
+
+exit_mod2 <- exit_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
+
+voice_mod1 <- exit_mod1 %>% update(PROJECT_VOICE~.+ PAST_VOICE)
+voice_mod2 <- voice_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
+
+work_mod1 <- exit_mod1 %>% update(PROJECT_EFFORT~.+ PAST_EFFORT)
+work_mod2 <- work_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
+
+sjPlot::tab_model(exit_mod1,exit_mod2,
+                  voice_mod1,voice_mod2,
+                  work_mod1,work_mod2,
+                  show.est = F,
+                  show.ci = F,
+                  show.se = T,
+                  show.std = T,
+                  collapse.se = T,
+                  emph.p=F,
+                  string.est = "B",
+                  string.std = "Beta",
+                  string.pred = " ",
+                  string.intercept = "Intercept",
+                  pred.labels = predictor_labels,
+                  dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2),
+                  order.terms = c(2,5:6,3:4,7:8,1))
+
+```
+
+## Heterogenious effects of backsliding, models with interactions (Online appendix A9)
+
+Interaction with individual level variables
+```{r}
+exit_mod1 <- lm(INTENT_EXIT_2 ~ 
+            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
+            data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))
+
+voice_mod1 <- exit_mod1 %>% update(PROJECT_VOICE~.+ PAST_VOICE)
+
+work_mod1 <- exit_mod1 %>% update(PROJECT_EFFORT~.+ PAST_EFFORT)
+
+```
+
+Seniority
+
+```{r}
+exit_mod1_ranking_interaction <- exit_mod1 %>% update(.~.+ BACKSLIDING_2*ranking)
+voice_mod1_ranking_interaction <- voice_mod1 %>% update(.~.+ BACKSLIDING_2*ranking)
+work_mod1_ranking_interaction <- work_mod1 %>% update(.~.+ BACKSLIDING_2*ranking)
+
+sjPlot::tab_model(exit_mod1_ranking_interaction,
+                  voice_mod1_ranking_interaction,
+                  work_mod1_ranking_interaction,
+                  show.est = F,
+                  show.ci = F,
+                  show.se = F,
+                  show.std = T,
+                  collapse.se = T,
+                  emph.p=F,
+                  string.est = "B",
+                  string.std = "Beta",
+                  string.pred = " ",
+                  string.intercept = "Intercept",
+                  pred.labels = predictor_labels,
+                                    dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=1))
+```
+
+```{r}
+anova(exit_mod1_ranking_interaction)
+anova(voice_mod1_ranking_interaction)
+anova(work_mod1_ranking_interaction)
+```
+
+```{r}
+sjPlot::plot_model(work_mod1_ranking_interaction,type="int")
+```
+
+Tenure
+
+```{r}
+exit_mod1_tenure_interaction <- exit_mod1 %>% update(.~.+ BACKSLIDING_2*tenure)
+voice_mod1_tenure_interaction <- voice_mod1 %>% update(.~.+ BACKSLIDING_2*tenure)
+work_mod1_tenure_interaction <- work_mod1 %>% update(.~.+ BACKSLIDING_2*tenure)
+
+sjPlot::tab_model(exit_mod1_tenure_interaction,
+                  voice_mod1_tenure_interaction,
+                  work_mod1_tenure_interaction,
+                  show.est = F,
+                  show.ci = F,
+                  show.se = F,
+                  show.std = T,
+                  collapse.se = T,
+                  emph.p=F,
+                  string.est = "B",
+                  string.std = "Beta",
+                  string.pred = " ",
+                  string.intercept = "Intercept",
+                  pred.labels = predictor_labels,
+                                    dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=1))
+```
+
+```{r}
+anova(exit_mod1_tenure_interaction)
+anova(voice_mod1_tenure_interaction)
+anova(work_mod1_tenure_interaction)
+```
+
+Education
+
+```{r}
+t1 <- data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE) %>% 
+  filter(education!="high-school")
+
+exit_mod1_education_interaction <- exit_mod1 %>% update(.~.+ BACKSLIDING_2*education,data=t1)
+voice_mod1_education_interaction <- voice_mod1 %>% update(.~.+ BACKSLIDING_2*education,data=t1)
+work_mod1_education_interaction <- work_mod1 %>% update(.~.+ BACKSLIDING_2*education,data=t1)
+
+sjPlot::tab_model(exit_mod1_education_interaction,
+                  voice_mod1_education_interaction,
+                  work_mod1_education_interaction,
+                  show.est = F,
+                  show.ci = F,
+                  show.se = F,
+                  show.std = T,
+                  collapse.se = T,
+                  emph.p=F,
+                  string.est = "B",
+                  string.std = "Beta",
+                  string.pred = " ",
+                  string.intercept = "Intercept",
+                  pred.labels = predictor_labels,
+                                    dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=1))
+```
+
+```{r}
+anova(exit_mod1_education_interaction)
+anova(voice_mod1_education_interaction)
+anova(work_mod1_education_interaction)
+```
+
+Legal education background (jurist)
+
+```{r}
+exit_mod1_jurist_interaction <- exit_mod1 %>% update(.~.+ BACKSLIDING_2*jurist)
+voice_mod1_jurist_interaction <- voice_mod1 %>% update(.~.+ BACKSLIDING_2*jurist)
+work_mod1_jurist_interaction <- work_mod1 %>% update(.~.+ BACKSLIDING_2*jurist)
+
+sjPlot::tab_model(exit_mod1_jurist_interaction,
+                  voice_mod1_jurist_interaction,
+                  work_mod1_jurist_interaction,
+                  show.est = F,
+                  show.ci = F,
+                  show.se = F,
+                  show.std = T,
+                  collapse.se = T,
+                  emph.p=F,
+                  string.est = "B",
+                  string.std = "Beta",
+                  string.pred = " ",
+                  string.intercept = "Intercept",
+                  pred.labels = predictor_labels,
+                                    dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=1))
+```
+
+```{r}
+anova(exit_mod1_jurist_interaction)
+anova(voice_mod1_jurist_interaction)
+anova(work_mod1_jurist_interaction)
+```
+
+Age
+
+```{r}
+exit_mod1_age_interaction <- exit_mod1 %>% update(.~.+ BACKSLIDING_2*age)
+voice_mod1_age_interaction <- voice_mod1 %>% update(.~.+ BACKSLIDING_2*age)
+work_mod1_age_interaction <- work_mod1 %>% update(.~.+ BACKSLIDING_2*age)
+
+sjPlot::tab_model(exit_mod1_age_interaction,
+                  voice_mod1_age_interaction,
+                  work_mod1_age_interaction,
+                  show.est = F,
+                  show.ci = F,
+                  show.se = F,
+                  show.std = T,
+                  collapse.se = T,
+                  emph.p=F,
+                  string.est = "B",
+                  string.std = "Beta",
+                  string.pred = " ",
+                  string.intercept = "Intercept",
+                  pred.labels = predictor_labels,
+                                    dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=1))
+```
+
+```{r}
+anova(exit_mod1_age_interaction)
+anova(voice_mod1_age_interaction)
+anova(work_mod1_age_interaction)
+```
+
+Gender
+
+```{r}
+exit_mod1_gender_interaction <- exit_mod1 %>% update(.~.+ BACKSLIDING_2*gender)
+voice_mod1_gender_interaction <- voice_mod1 %>% update(.~.+ BACKSLIDING_2*gender)
+work_mod1_gender_interaction <- work_mod1 %>% update(.~.+ BACKSLIDING_2*gender)
+
+sjPlot::tab_model(exit_mod1_gender_interaction,
+                  voice_mod1_gender_interaction,
+                  work_mod1_gender_interaction,
+                  show.est = F,
+                  show.ci = F,
+                  show.se = F,
+                  show.std = T,
+                  collapse.se = T,
+                  emph.p=F,
+                  string.est = "B",
+                  string.std = "Beta",
+                  string.pred = " ",
+                  string.intercept = "Intercept",
+                  pred.labels = predictor_labels,
+                                    dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=1))
+```
+
+```{r}
+anova(exit_mod1_gender_interaction)
+anova(voice_mod1_gender_interaction)
+anova(work_mod1_gender_interaction)
+```
+
+Party by minister
+
+```{r}
+exit_mod1_ministry_by_party <- exit_mod1 %>% update(.~.+ ministry_by_party)
+exit_mod1_ministry_by_party_interaction <- exit_mod1 %>% update(.~.+ BACKSLIDING_2*ministry_by_party)
+
+voice_mod1_ministry_by_party <- voice_mod1 %>% update(.~.+ ministry_by_party)
+voice_mod1_ministry_by_party_interaction <- voice_mod1 %>% update(.~.+ BACKSLIDING_2*ministry_by_party)
+
+work_mod1_ministry_by_party <- work_mod1 %>% update(.~.+ ministry_by_party)
+work_mod1_ministry_by_party_interaction <- work_mod1 %>% update(.~.+ BACKSLIDING_2*ministry_by_party)
+
+sjPlot::tab_model(exit_mod1_ministry_by_party_interaction,
+                  voice_mod1_ministry_by_party_interaction,
+                  work_mod1_ministry_by_party_interaction,
+                  show.est = F,
+                  show.ci = F,
+                  show.se = F,
+                  show.std = T,
+                  collapse.se = T,
+                  emph.p=F,
+                  string.est = "B",
+                  string.std = "Beta",
+                  string.pred = " ",
+                  string.intercept = "Intercept",
+                  pred.labels = predictor_labels,
+                                    dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=1))
+```
+
+```{r}
+anova(exit_mod1_ministry_by_party_interaction)
+anova(voice_mod1_ministry_by_party_interaction)
+anova(work_mod1_ministry_by_party_interaction)
+```
